### 2012-10-25 paper/mswp2012-proposal.tex
added template

\documentclass[a4paper,11pt]{article}

\usepackage{graphicx}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% \usepackage{mathptmx} % Times New Roman

\setlength{\topmargin}{-0.4mm} % (1in=25.4mm)-0.4mm=25mm
\setlength{\textheight}{243.119mm} % 297mm-40mm-10mm-(11pt=3.881mm)=
\setlength{\oddsidemargin}{-0.4mm} % (1in=25.4mm)-0.4mm=25mm
\setlength{\textwidth}{160mm} % 210mm-50mm=160mm
\setlength{\headheight}{0mm}
\setlength{\headsep}{0mm}
\setlength{\footskip}{15mm}

\providecommand*{\note}[1]{\small \textcolor{RoyalBlue}{\begin{minipage}{\textwidth}{#1}\end{minipage}}}

% --------------------------------------------------------------

\providecommand*{\ShortTitle}{$<$Short title$>$}
\providecommand*{\FullTitle}{$<$Full title$>$}

% --------------------------------------------------------------

\title{\textbf{\sffamily\Huge \ShortTitle}\\ 
{\textbf{\sffamily\Large \FullTitle}}
\vspace{1cm}}

\author{
{\em 188.407: Management von Software Projekten} \vspace{1cm} \\
Group: $<$GID$>$\bigskip \\
$<$Author1$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author1@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author2$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author2@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author3$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author3@tuwien.ac.at}{author1@tuwien.ac.at}}\\
$<$Author4$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author4@tuwien.ac.at}{author1@tuwien.ac.at}}\\ 
\vspace{4cm}
}

\begin{document}

\begin{titlepage}
\maketitle

\end{titlepage}

% --------------------------------------------------------------

\thispagestyle{empty}
\tableofcontents
\pagebreak

\setcounter{page}{1}

% --------------------------------------------------------------

\note{
\textbf{Formal constraints}
\begin{itemize}
\item	  Font: Times New Roman oder Computer Modern (\LaTeX default)
\item    Fontsize: 11pt
\item     Single line spacing
\item     Margins: 2.5cm side and top/bottom
\item     \fbox{Language: ENGLISH}
\item    The proposal template should be filled incrementally. I.e., at the end there should be a full project proposal in a single PDF file.
\end{itemize}
\textbf{Available templates}
\begin{itemize}
\item     Proposal (mswp-proposal.tex)
\item     Costs (costs.xls, costs.ods)
\end{itemize}
\textbf{Supplemental material}
\begin{itemize}
\item     FWF salary scheme (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
\item     Travel cost regulation (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html})
\item     Ethical issues form (ethical-issues.rtf)
\end{itemize}
}
\pagebreak

% --------------------------------------------------------------
\section{Synopsis}
\label{sect:synopsis}

\note{
\begin{itemize}
	\item {\em Length: 1-2 pages}
	\item Concise presentation of the scientific proposal, with particular attention to the ground-breaking nature of the research project, which will allow to assess the feasibility of the outlined scientific approach. 
	\item WHY would you like to do WHAT, HOW would you like to do it and what are the expected RESULTS?
	\item Short description of project idea.
	\item Short description of problem / situation.
	\item What makes it an interesting endeavor?
	\item Why should somebody care?
	\item Very short cost-benefit description (what are potential benefits that make them worth the costs of the project?).
	\item Who are the beneficiaries of the results?
	\item Problem classification (to which scientific area does the project belong?; is it basic or applied research?)
	\item Constraints
	\begin{itemize}
		\item     The project must have an extent that demands to handle it as a project including project organization.  (No 2 person pieces; no 150 person-year efforts)
		\item     Software development should be part of the project. (But not its only content or scientific contribution.)
		\item     The project should be interesting and meaningful.
		\item     {\em Your creativity is called for!!}
	\end{itemize}
\end{itemize}
}

% --------------------------------------------------------------
\section{Introduction and problem description}
\label{sect:intro}

\note{
\begin{itemize}
	\item {\em Length: 2-3 pages}
	\item {\bf Why?}
	\item Introduction
	\item Context
	\item What is the current situation?
	\item What is the open/unresolved problem or opportunity?
	\item Why is it a problem?
	\item What is unknown?
	\item What could be improved?
	\item Explanation of fundamental terms and basic definitions.
\end{itemize}
}

% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

\note{
\begin{itemize}
	\item {\em Length: 1-2 pages}
	\item What is the goal of the project?
	\item Research questions
	\begin{itemize}
		\item 	    What are the hypotheses that are to be investigated?
		\item 	    Main hypothesis \& sub hypotheses
	\end{itemize}
	\item Which results should be achieved with the project?
	\begin{itemize}
	    	\item 	   What will be known afterwards that is not known now?
		\item	    What will be created that does not exist now?
	\end{itemize}
	\item Non-goals (What will not be part of the project? What will not be done?)
\end{itemize}
}

% --------------------------------------------------------------
\section{Scientific relevance and innovative aspects}
\label{sect:relevance}

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Why is the project scientifically interesting?
\item Did others point out that this is an open question?
\item What are the innovative aspects that make it interesting?
\item How could the project break new ground scientifically?
\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
\end{itemize}
}

% --------------------------------------------------------------
\section{State of the art / current knowledge}
\label{sect:star}

\note{
\begin{itemize}
\item {\em Length: 2-5 pages}
\item What results and approaches have already been presented in this or related areas?
\item Relation to the international scientific work in the field (international status of the research)
\item Description and critical discussion of related scientific work
\end{itemize}
}

% --------------------------------------------------------------
\section{Method}
\label{sect:method}

\note{
\begin{itemize}
\item {\em Length: 2-5 pages}
\item {\bf How?}
\item How should the expected results be achieved?
\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
\item Description of the methods.
\item Justifications for chosen methods.
\end{itemize}
}

% --------------------------------------------------------------
\section{Detailed description of the workpackages}
\label{sect:workplan}

\note{
\begin{itemize}
\item {\em Length: 2-4 pages}
\item Structuring the project into self-contained parts.
\item Additional verbal descriptions.
\item Work packages
    \begin{itemize}
    \item title
    \item goal(s)
    \item description
    \item expected results
    \item responsible person(s)
    \item dependencies
    \end{itemize}
\end{itemize}
}

% --------------------------------------------------------------
\section{Time plan (Gantt chart)}
\label{sect:timeplan}

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Realistic estimation of schedule based on workpackages.
\item Including milestones (not only when but also what is to be achieved for each milestone).
\item Generation of a Gantt chart. (Including phases, milestones, buffer times, critical areas, etc.)
\end{itemize}
}

% --------------------------------------------------------------
\section{Human resources / team}
\label{sect:team}

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Description of the team that is needed to carry out the project. (For the execution phase of the project, not the planning phase.)
\item How many people?
\item To what extent are individual members needed?
\item What knowledge, skills, and experiences are needed for each member?
\item Demonstrate that the members will be able to carry out the project successfully.
\item Work structure
	\begin{itemize}
	\item     Who will lead the project?
	\item     How do they work together?
	\item     Management and coordination
		\begin{itemize}
		\item 	        What communication structures will be established? (e.g., mailing list, blog, CMS, CVS, ...)
		\item 	        How often will meetings take place? (Who will participate?)
		\item 	        How will the work be documented?
		\item 	        How will information be stored and shared?
		\end{itemize}
	\end{itemize}
\item Cooperations
	\begin{itemize}
	\item     Will external cooperators be part of the project? (e.g., other research institutions or companies)
	\item     What is their role?
	 \item    Why are they needed?
	\end{itemize}
\end{itemize}
}

% --------------------------------------------------------------
\section{Costs}
\label{sect:costs}

\note{
\begin{itemize}
\item {\em Length: 2-3 pages}
\item Rough estimation of cost in form of calculation (table(s)) + descriptive text.
\item Justification for the personnel and non-personnel costs (equipment, material, travel and other costs)
\item An Excel template is provided as supplementary material to support budgeting.
\item Personnel costs
	\begin{itemize}
	\item     Justification for the personnel to be assigned to the project (type of position(s), description of nature of work, length and extent of involvement in the project)
	\item     The application should include all persons who will be required for the proposed project (project lead, researchers, developers, advisory board, etc.). The available legal categories of employment are contracts of employment for full- or part-time employees (DV) and reimbursement for work on an hourly basis (GB). In addition, a part-time contract of employment (DV 50\%, ``studentische Mitarbeiter'') may be requested for people who have not yet completed a Master or Diploma program (Diplom) in the relevant subject.
	 \item    The justification of the requested personnel should contain:
		\begin{itemize}
		\item 	        description of type of work;
		\item 		        extent of involvement (part-time contracts are permitted).
		\end{itemize}
	\item Exact numbers of employment categories can be found on the FWF Website (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
	\end{itemize}
\item Equipment costs
	\begin{itemize}
	\item     Indicate reasons for equipment costs. The ``scientific equipment'' category includes instruments, system components, costs for the use of software required by the project and other durable goods provided the cost per item (including VAT) exceeds EUR 1,500.00.
	\end{itemize}
\item Material costs
	\begin{itemize}
	\item     This category encompasses consumables and smaller pieces of equipment where the cost per item is below EUR 1,500.00 including VAT. The calculation of requested material costs should be justified with reference to the schedule, work plan and experimental plan. Experience with previous projects should be taken into account.
	\end{itemize}
\item Travel costs
	\begin{itemize}
	\item     Funding may be requested for the costs of project-specific travel and accommodation, field work, expeditions, etc. Applicants are to provide a detailed travel (cost) plan broken down by project participant. For brief stays, the calculation of the travel and accommodation costs should be based on the federal regulations governing travel costs (RGV). The RGV rates governing Austria and abroad may be found in the FAQs on the FWF Website (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}). For longer stays an appropriate and comprehensible cost plan should be prepared.
	\end{itemize}
\item Other costs
	\begin{itemize}
	\item     Independent contracts for work and services (costs for work of clearly defined scope and content assigned to individuals, provided that this is scientifically justifiable and economical)
    	\item     Costs that cannot be included under personnel, equipment, material or travel costs, such as:
		\begin{itemize}
		\item         reimbursement of costs towards or for the use of research facilities, e.g. of large-scale research facilities (project-specific 'equipment time'). Applicants should obtain and submit multiple offers;
		\item         costs for project-specific work carried out outside the applicant's research institution (e.g. for analysis work performed elsewhere, for interviews, for sample collection, for preparation of thin slices etc.). Applicants should obtain and submit multiple offers;
		\item         honoraria for test persons;
		\end{itemize}
	\end{itemize}
\end{itemize}
}

% --------------------------------------------------------------
\section{Expected implications and risks}
\label{sect:implication-risk}

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Importance of the expected results for the discipline
	\begin{itemize}
	\item     To what extent does the proposed research address important challenges?
	\end{itemize}
\item Importance of the expected results for other areas
\item What are possible risks of the project and how can they be alleviated?
	\begin{itemize}
	\item     What factors could lead to a failure of the project?
	\item     Which factors or persons could support the project and increase the chance for success?
	\item     What if important team members leave the project?
	\end{itemize}
\end{itemize}
}

% --------------------------------------------------------------
\section{Ethical considerations \& security issues}
\label{sect:ethics-security}

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
\item Are there any security-sensitive issues that apply to your proposal?
\end{itemize}
}

% --------------------------------------------------------------
% APPENDIX
\begin{appendix}

\pagebreak

% --------------------------------------------------------------
% References
\phantomsection
\addcontentsline{toc}{section}{References}

\bibliographystyle{apalike}
\bibliography{mswp2012-proposal}

\pagebreak

% --------------------------------------------------------------
% Abbreviations
\section*{Abbreviations}
 \addcontentsline{toc}{section}{Abbreviations}

 \begin{description}
  \item[MSWP] Management von Software Projekten
  \item[WP] Work Package
 \end{description}

\end{appendix}

\end{document}

### 2012-10-25 paper/mswp2012-proposal.tex
first version of Proposal (in German)

@@
 
-\note{
+% \note{
+%\begin{itemize}
+%	\item {\em Length: 1-2 pages}
+%	\item Concise presentation of the scientific proposal, with particular attention to the ground-breaking nature of the research project, which will allow to assess the feasibility of the outlined scientific approach.
+%	\item WHY would you like to do WHAT, HOW would you like to do it and what are the expected RESULTS?
+%	\item Short description of project idea.
+%	\item Short description of problem / situation.
+%	\item What makes it an interesting endeavor?
+%	\item Why should somebody care?
+%	\item Very short cost-benefit description (what are potential benefits that make them worth the costs of the project?).
+%	\item Who are the beneficiaries of the results?
+%	\item Problem classification (to which scientific area does the project belong?; is it basic or applied research?)
+%	\item Constraints
+%	\begin{itemize}
+%		\item     The project must have an extent that demands to handle it as a project including project organization.  (No 2 person pieces; no 150 person-year efforts)
+%		\item     Software development should be part of the project. (But not its only content or scientific contribution.)
+%		\item     The project should be interesting and meaningful.
+%		\item     {\em Your creativity is called for!!}
+%	\end{itemize}
+%\end{itemize}
+%}
+
+Das Projekt verfolgt das Ziel eine Plattform im Bereich e-Health zu schaffen.
+Diese Platform soll für die Nutzer ein Bonus-System bereitstellen und die Möglichkeit bieten herauszufinden, wie gesund die einzelnen Nutzer leben.\\
+
+Das Projekt wird hierbei in verschiedene Phasen aufgeteilt, die eine langfristige Weiterentwicklung möglich machen bzw.
+mögliche Ausbaustufen aufzeigen.
+Für jeden der Phasen müssen Vertragspartner gefunden werden, die sich an der Plattform beteiligen.
+Diese Vertragspartner versorgen die Nutzer mit Boni und bekommen als Benefit eine Steigerung der Kundenbindung bzw.
+eine Möglichkeit Werbepräsenz auf der Plattform zu ergattern.\\
+
+Mögliche Vertragspartner sind:
 \begin{itemize}
-	\item {\em Length: 1-2 pages}
-	\item Concise presentation of the scientific proposal, with particular attention to the ground-breaking nature of the research project, which will allow to assess the feasibility of the outlined scientific approach.
-	\item WHY would you like to do WHAT, HOW would you like to do it and what are the expected RESULTS?
-	\item Short description of project idea.
-	\item Short description of problem / situation.
-	\item What makes it an interesting endeavor?
-	\item Why should somebody care?
-	\item Very short cost-benefit description (what are potential benefits that make them worth the costs of the project?).
-	\item Who are the beneficiaries of the results?
-	\item Problem classification (to which scientific area does the project belong?; is it basic or applied research?)
-	\item Constraints
+	\item Phase 1:
 		\begin{itemize}
-		\item     The project must have an extent that demands to handle it as a project including project organization.  (No 2 person pieces; no 150 person-year efforts)
-		\item     Software development should be part of the project. (But not its only content or scientific contribution.)
-		\item     The project should be interesting and meaningful.
-		\item     {\em Your creativity is called for!!}
+			\item Supermärkte
+			\item Fitness-Center
+			\item Restaurants
+		\end{itemize}
+	\item Phase 2 - \"Einbindung bestehender Services\":
+		\begin{itemize}
+			\item Laufplattformen mit Tracking (Runtastic, RunKeeper, etc.)
+			\item andere Sporttracking-Services (Schrittzähler, etc.)
+		\end{itemize}
+	\item Phase 3 - \"Health Organisations\":
+		\begin{itemize}
+			\item Versicherungsunternehmen
 		\end{itemize}
 \end{itemize}
-}
+
+Die Nutzer haben die Möglichkeit beim Einkauf oder Konsumation bei einem der Vertragspartner selbiges über eine App registrieren lassen.
+Im System werden dann anonymisiert die Einkäufe in Kategorien gespeichert und nach einem vorgefertigtem transparenten Punkteschmea bewertet.\\
+
+Die Punkte können nach einer bestimmten Zeitspanne durch Gutscheine eingelöst werden, die dann bei den Vertragspartnern wieder eingelöst werden können.
+Ebenso können über die Plattformen Rankings und Verlosungen vorgenommen werden.
+Die Vertragspartner können die Nutzer über die App über neue Aktionen informieren, über die Zusatzpunkte erworben werden können.
+
+\pagebreak
 

### 2012-10-25 paper/mswp2012-proposal.tex
added Goals to Synopsis

@@
 Ebenso können über die Plattformen Rankings und Verlosungen vorgenommen werden.
-Die Vertragspartner können die Nutzer über die App über neue Aktionen informieren, über die Zusatzpunkte erworben werden können.
+Die Vertragspartner können die Nutzer über die App über neue Aktionen informieren, über die Zusatzpunkte erworben werden können.\\
+
+Die Plattform verfolgt folgende Ziele:
+\begin{itemize}
+	\item \textbf{Gesundheit der Nutzer}: Das Gesundheitsbewusstsein wächst in der Bevölkerung immer stärker an, gesünder zu leben wird zum wichtigen Ziel.
+Das Gesundheitssystem verschlingt trotzdem jährlich Unsummen an Geld, somit gibt es auch von dieser Seite ein großes Interesse an der Gesundheit der Bevölkerung.
+	\item \textbf{Werbepositionen}: Vertragspartner bietet die Plattform eine Möglichkeit Werbung zu positionieren.
+Durch die Verteilung von Rabatt-Coupons, die natürlich auch mit einem Ablaufdatum gekoppelt werden können, wird eine Kundenbindung hervorgerufen und der Nutzer animiert, wieder den Vertragspartner für ein Konsumation aufzusuchen.
+Zusätzlich soll über die Vertragspartner Geld für die Finanzierung der Plattform zur Verfügung gestellt werden.
+	\item \textbf{Vergünstigungen für Nutzer}: Die Nutzer sollen durch die Nutzung der Plattform einen neben der Kontroller über ihren Lebensstil auch Vergünstigungen der Vertragspartner erhalten.
+Dieser kann zum Beispiel über Rabattcoupons erfolgen.
+\end{itemize}
 

### 2012-10-25 paper/mswp2012-proposal.tex
fixed doppelquotes and added Name to first Page

@@
 {\em 188.407: Management von Software Projekten} \vspace{1cm} \\
-Group: $<$GID$>$\bigskip \\
-$<$Author1$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author1@tuwien.ac.at}{author1@tuwien.ac.at}}\\
+Group: 12\bigskip \\
+Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@tuwien.ac.at}{e0728061@tuwien.ac.at}}\\
 $<$Author2$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author2@tuwien.ac.at}{author1@tuwien.ac.at}}\\
@@
 		\end{itemize}
-	\item Phase 2 - \"Einbindung bestehender Services\":
+	\item Phase 2 - $"$Einbindung bestehender Services$"$:
 		\begin{itemize}
@@
 		\end{itemize}
-	\item Phase 3 - \"Health Organisations\":
+	\item Phase 3 - $"$Health Organisations$"$:
 		\begin{itemize}

### 2012-10-27 paper/mswp2012-proposal.tex
englisch (zumindest versucht :) )

--- 2012-10-25 paper/mswp2012-proposal.tex
@@
 
-\providecommand*{\ShortTitle}{$<$Short title$>$}
+\providecommand*{\ShortTitle}{Modern voluntary health-care-system}
 \providecommand*{\FullTitle}{$<$Full title$>$}
@@
 {\em 188.407: Management von Software Projekten} \vspace{1cm} \\
-Group: $<$GID$>$\bigskip \\
-$<$Author1$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author1@tuwien.ac.at}{author1@tuwien.ac.at}}\\
-$<$Author2$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author2@tuwien.ac.at}{author1@tuwien.ac.at}}\\
+Group: 12\bigskip \\
+Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\
+Dominik Oberhumer \\ {\small 1025454, 033 534, \href{mailto:e1025454@student.tuwien.ac.at}{e1025454@student.tuwien.ac.at}}\\
 $<$Author3$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author3@tuwien.ac.at}{author1@tuwien.ac.at}}\\
@@
 
-\note{
-\textbf{Formal constraints}
-\begin{itemize}
-\item	  Font: Times New Roman oder Computer Modern (\LaTeX default)
-\item    Fontsize: 11pt
-\item     Single line spacing
-\item     Margins: 2.5cm side and top/bottom
-\item     \fbox{Language: ENGLISH}
-\item    The proposal template should be filled incrementally. I.e., at the end there should be a full project proposal in a single PDF file.
-\end{itemize}
-\textbf{Available templates}
-\begin{itemize}
-\item     Proposal (mswp-proposal.tex)
-\item     Costs (costs.xls, costs.ods)
-\end{itemize}
-\textbf{Supplemental material}
-\begin{itemize}
-\item     FWF salary scheme (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
-\item     Travel cost regulation (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html})
-\item     Ethical issues form (ethical-issues.rtf)
-\end{itemize}
-}
-\pagebreak
+%\note{
+%\textbf{Formal constraints}
+%\begin{itemize}
+%\item	  Font: Times New Roman oder Computer Modern (\LaTeX default)
+%\item    Fontsize: 11pt
+%\item     Single line spacing
+%\item     Margins: 2.5cm side and top/bottom
+%\item     \fbox{Language: ENGLISH}
+%\item    The proposal template should be filled incrementally. I.e., at the end there should be a full project proposal in a single PDF file.
+%\end{itemize}
+%\textbf{Available templates}
+%\begin{itemize}
+%\item     Proposal (mswp-proposal.tex)
+%\item     Costs (costs.xls, costs.ods)
+%\end{itemize}
+%\textbf{Supplemental material}
+%\begin{itemize}
+%\item     FWF salary scheme (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}%{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
+%\item     Travel cost regulation (\href{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html}{http://www.fwf.ac.at/de/faq/reisegebuehrenvorschrift.html})
+%\item     Ethical issues form (ethical-issues.rtf)
+%\end{itemize}
+%}
+%\pagebreak
 
@@
 
-Das Projekt verfolgt das Ziel eine Plattform im Bereich e-Health zu schaffen.
-Diese Platform soll für die Nutzer ein Bonus-System bereitstellen und die Möglichkeit bieten herauszufinden, wie gesund die einzelnen Nutzer leben.\\
+The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system for the users. So the users are able to find out how healthy they life. \\
 
-Das Projekt wird hierbei in verschiedene Phasen aufgeteilt, die eine langfristige Weiterentwicklung möglich machen bzw.
-mögliche Ausbaustufen aufzeigen.
-Für jeden der Phasen müssen Vertragspartner gefunden werden, die sich an der Plattform beteiligen.
-Diese Vertragspartner versorgen die Nutzer mit Boni und bekommen als Benefit eine Steigerung der Kundenbindung bzw.
-eine Möglichkeit Werbepräsenz auf der Plattform zu ergattern.\\
+The project is split into different phases.
+This enables a useable product after a short time but the vision is a long-term development.
+For each phase it is necessary to find different partner in economy and politics.
+The partners use the platform for advertisement and for costumer relationship.
+So the partners have benefits too.
+\\
 
-Mögliche Vertragspartner sind:
+Possible Partners are:
 \begin{itemize}
@@
 		\begin{itemize}
-			\item Supermärkte
-			\item Fitness-Center
+			\item Supermarkets
+			\item Fitness-Centers
 			\item Restaurants
 		\end{itemize}
-	\item Phase 2 - \"Einbindung bestehender Services\":
+	\item Phase 2 - $"$Embedding to existing services$"$:
 		\begin{itemize}
-			\item Laufplattformen mit Tracking (Runtastic, RunKeeper, etc.)
-			\item andere Sporttracking-Services (Schrittzähler, etc.)
+			\item Sport-Community with Tracking (Runtastic, RunKeeper, etc.)
+			\item other Sporttracking-Services (Pedometer, etc.)
 		\end{itemize}
-	\item Phase 3 - \"Health Organisations\":
+	\item Phase 3 - $"$Health Organisations$"$:
 		\begin{itemize}
-			\item Versicherungsunternehmen
+			\item Insurances 
 		\end{itemize}
@@
 
-Die Nutzer haben die Möglichkeit beim Einkauf oder Konsumation bei einem der Vertragspartner selbiges über eine App registrieren lassen.
-Im System werden dann anonymisiert die Einkäufe in Kategorien gespeichert und nach einem vorgefertigtem transparenten Punkteschmea bewertet.\\
+When a user buys something in a shop of a partner he can register the products within an App. In the System the consummations get anonymised saved and analyzed based on a transparent score-schema. \\
 
-Die Punkte können nach einer bestimmten Zeitspanne durch Gutscheine eingelöst werden, die dann bei den Vertragspartnern wieder eingelöst werden können.
-Ebenso können über die Plattformen Rankings und Verlosungen vorgenommen werden.
-Die Vertragspartner können die Nutzer über die App über neue Aktionen informieren, über die Zusatzpunkte erworben werden können.
+The user can exchange the scores for gifts like coupons for healthy shopping by a partner.
+Moreover the platform can be used for rankings (which of the user live most healthy?) and lotteries.
+The partner can interact with the user over the platform.
+So they can advertise new promotions.
+This promotion can be used by the user for getting additional scores.
+\\
+
+The goals of the platform:
+\begin{itemize}
+\item \textbf{Health of the User}: The peoples are getting more sensible for health-care.
+So they are going to live in a healthier way.
+The healthcare-system is very expansive.
+So the whole government will have a benefit from this platform and more healthier people.
+\item \textbf{Advertisment for the Partner}: For the partner the platform offers a chance to advertise their promotions.
+Furthermore they have the chance to spend coupons to the user.
+With this coupon they can interact with the costumer.
+So the customer loyalty is getting gain.
+The costumer is getting animated to buy more by partners.
+For this the partner has to refinance a part of the platform.
+\item \textbf{Benefits for User}: The User should get cheaper prices, when they buy some healthy things within partner stores. For example the coupons from an lottery in this platform.
+
+\end{itemize}
 

### 2012-10-29 paper/mswp2012-proposal.tex
Added another organization example and students

@@
 Group: 12\bigskip \\
-Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\
 Dominik Oberhumer \\ {\small 1025454, 033 534, \href{mailto:e1025454@student.tuwien.ac.at}{e1025454@student.tuwien.ac.at}}\\
-$<$Author3$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author3@tuwien.ac.at}{author1@tuwien.ac.at}}\\
-$<$Author4$>$ \\ {\small $<$Matrikelnr.$>$, $<$Kennzahl$>$, \href{mailto:author4@tuwien.ac.at}{author1@tuwien.ac.at}}\\ 
+Gerhard Schraml \\ {\small 0728067, 033 534, \href{mailto:e0728067@student.tuwien.ac.at}{e0728067@student.tuwien.ac.at}}\\
+Johannes Kurz \\ {\small 0727957, 033534, \href{mailto:e0727957@student.tuwien.ac.at}{e0727957@student.tuwien.ac.at}}\\
+Matthias Tretter \\ {\small 0726390, 066 937,  \href{mailto:e0726390@student.tuwien.ac.at}{e0726390@student.tuwien.ac.at}}\\
+Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\
+
 \vspace{4cm}
@@
 			\item Insurances 
+			\item WHO
 		\end{itemize}

### 2012-10-30 paper/mswp2012-proposal.tex
corrected spelling mistakes... latex does not compile at my machine due to multiline \author command???

@@
 
-The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system for the users. So the users are able to find out how healthy they life. \\
+The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system to give users an easy-understandable overview on how healthy they live.\\
 
 The project is split into different phases.
-This enables a useable product after a short time but the vision is a long-term development.
-For each phase it is necessary to find different partner in economy and politics.
-The partners use the platform for advertisement and for costumer relationship.
+This leads to the creation of a useable, rudimentary product after a short time.
+Nevertheless, the vision is a long-term development.
+For each phase it is necessary to find different partners in economy and politics.
+The partners use the platform for advertisement and customer relationship.
 So the partners have benefits too.
@@
 
-When a user buys something in a shop of a partner he can register the products within an App. In the System the consummations get anonymised saved and analyzed based on a transparent score-schema. \\
+When a user buys something in a shop of a partner he can register the product within an app. In the system the purchases get anonymised, saved and analyzed based on a transparent score-schema. \\
 
-The user can exchange the scores for gifts like coupons for healthy shopping by a partner.
-Moreover the platform can be used for rankings (which of the user live most healthy?) and lotteries.
-The partner can interact with the user over the platform.
+The user can exchange the scores for gifts like coupons for healthy shopping at a partners store.
+Moreover the platform can be used for rankings (which of the user lives most healthy?) and lotteries.
+Partners are able to interact with the user over the platform.
 So they can advertise new promotions.
@@
 \begin{itemize}
-\item \textbf{Health of the User}: The peoples are getting more sensible for health-care.
-So they are going to live in a healthier way.
-The healthcare-system is very expansive.
+\item \textbf{Health of the user}: People are getting more sensible for health-care.
+So they get forced to live in a healthier way.
+The healthcare-system is very expensive.
 So the whole government will have a benefit from this platform and more healthier people.
-\item \textbf{Advertisment for the Partner}: For the partner the platform offers a chance to advertise their promotions.
-Furthermore they have the chance to spend coupons to the user.
-With this coupon they can interact with the costumer.
-So the customer loyalty is getting gain.
-The costumer is getting animated to buy more by partners.
-For this the partner has to refinance a part of the platform.
-\item \textbf{Benefits for User}: The User should get cheaper prices, when they buy some healthy things within partner stores. For example the coupons from an lottery in this platform.
+\item \textbf{Advertisement for the partners}: For the partners the platform offers a chance to advertise their promotions.
+Furthermore they have the chance to give coupons to the users.
+With this coupon they can interact with the customer.
+One possible effect is a gain in customer loyalty.
+The customer is getting animated to buy more at partners stores.
+Therefore partners have to refinance a part of the platform.
+\item \textbf{Benefits for users}: Users should be given discounts when they buy some healthy things at partners stores.
+This could be achieved by giving coupons to users from a lottery in the platform.
 

### 2012-11-06 paper/mswp2012-proposal.tex
extended synopsis by small science part

@@
 Philip Messlehner \\ {\small 0728061, 066 937, \href{mailto:e0728061@student.tuwien.ac.at}{e0728061@student.tuwien.ac.at}}\\
-
 \vspace{4cm}
@@
 
-% \note{
+%\note{
 %\begin{itemize}
@@
 
-The goal of the project is to create and publish an e-health platform. This platform is based on a bonus/malus system to give users an easy-understandable overview on how healthy they live.\\
+The ultimate goal of the Modern Voluntary Health-Care System is to create and publish an e-health platform.
+This platform is based on a bonus malus system to give users an easy-understandable overview on how healthy they live.\\
 
-The project is split into different phases.
-This leads to the creation of a useable, rudimentary product after a short time.
+Therefore the project is split in both a scientific and an engineering part.
+The scientific part aims at searching for technical methods to encourage people to live healthier.
+For this purpose we try to evaluate and answer some questions, such as:
+
+\begin{itemize}
+\item How can people, by technical means, be subconsciously forced to change their ways and daily routines?
+\item Is there a way to achieve practical improvements in peoples health by providing a playful approach to do so?
+\item Are those improvements comparable to e.g. consulting professionals such as nutritionists, health trainers or even doctors?
+\end{itemize}
+
+Case studies including user tests in the section of human-computer-interaction shall lead to a basis for developing a completely innovative and ground-breaking health-care system, which brings benefits to several different parties.\\
+
+The engineering part is split into different phases.
+This leads to the creation of a usable, rudimentary product after a short time.
 Nevertheless, the vision is a long-term development.

### 2012-11-06 paper/mswp2012-proposal.tex
Add full title

@@
 
-\providecommand*{\ShortTitle}{Modern voluntary health-care-system}
-\providecommand*{\FullTitle}{$<$Full title$>$}
+\providecommand*{\ShortTitle}{Modern voluntary Health-Care-System}
+\providecommand*{\FullTitle}{The influence of gamification on the willingness to live healthy}
 
@@
 Gerhard Schraml \\ {\small 0728067, 033 534, \href{mailto:e0728067@student.tuwien.ac.at}{e0728067@student.tuwien.ac.at}}\\
-Johannes Kurz \\ {\small 0727957, 033534, \href{mailto:e0727957@student.tuwien.ac.at}{e0727957@student.tuwien.ac.at}}\\
+Johannes Kurz \\ {\small 0727957, 033 534, \href{mailto:e0727957@student.tuwien.ac.at}{e0727957@student.tuwien.ac.at}}\\
 Matthias Tretter \\ {\small 0726390, 066 937,  \href{mailto:e0726390@student.tuwien.ac.at}{e0726390@student.tuwien.ac.at}}\\

### 2012-11-06 paper/mswp2012-proposal.tex
Several grammatic fixes, more information about scientific part

@@
 
-The ultimate goal of the Modern Voluntary Health-Care System is to create and publish an e-health platform.
-This platform is based on a bonus malus system to give users an easy-understandable overview on how healthy they live.\\
+The ultimate goal of the Modern Voluntary Health-Care System is to create and publish a new form of an e-health system that encourages users to live healthy.
+This platform is based on a bonus malus system to give users an easy understandable overview on how healthy they live and how they compare to others.
+\\
 
-Therefore the project is split in both a scientific and an engineering part.
-The scientific part aims at searching for technical methods to encourage people to live healthier.
+The project is split in both a scientific and an engineering part.
+The scientific part aims at searching for technical methods to encourage people to live healthier and generating knowledge of the influence of gamification on the willingness of people to live healthy.
+From a scientific perspective it is interesting to see how well-known methods like gamification and competition can be used to motivate people to live and stay healthy.
+
 For this purpose we try to evaluate and answer some questions, such as:
@@
 \item Are those improvements comparable to e.g. consulting professionals such as nutritionists, health trainers or even doctors?
+\item Does competition motivate people to stay healthy?
 \end{itemize}
 
-Case studies including user tests in the section of human-computer-interaction shall lead to a basis for developing a completely innovative and ground-breaking health-care system, which brings benefits to several different parties.\\
+The knowledge generated from these tests and questions can be used as a scientific backbone on the journey to a more healthy and fit society.
+From a psychological perspective it's important to generate data on how gamification of all-day tasks like eating, walking and avoiding health traps can improve the attitude and willingness of people to live healthy.
+Combined with a modern workflow and easy tracking of health-related data by offering a mobile interface our study aims at generating new knowledge in the field of gamification through technology.
+Moreover the study should reveal useful information on the usability and user interface of such a system.
+A clunky interface and no support for automatic tracking of information ultimately means a failure of the whole system.
+Is is vital to generate useful and accurate data of each participant because the system stays and fails with the usefulness of the collected data.
+We can't force the user to manually enter each and every task he does throughout the day, we need to automate this process as much as possible and we need to integrate with other tracking systems to get access to even more data.
+The interface of the modern health-care system should stay out of the way of the user, it should intelligently track the information needed to generate good statistics of the habits of the participant.
+
+Case studies including user tests in the section of human computer interaction shall lead to a basis for developing a completely innovative and ground-breaking health-care system, which brings benefits to several different parties.\\
 
 The engineering part is split into different phases.
-This leads to the creation of a usable, rudimentary product after a short time.
+This leads to the creation of a usable, rudimentary but integrated prototype after a short time.
 Nevertheless, the vision is a long-term development.
-For each phase it is necessary to find different partners in economy and politics.
-The partners use the platform for advertisement and customer relationship.
-So the partners have benefits too.
+For each phase it is necessary to find different partners in economy, politics, health-care and science.
+The partners mainly use our platform for advertisement and customer relationships, which brings benefits to them as well.
 \\
@@
 			\item Supermarkets
-			\item Fitness-Centers
+			\item Fitness Centers
 			\item Restaurants
+			\item Doctors
 		\end{itemize}
-	\item Phase 2 - $"$Embedding to existing services$"$:
+	\item Phase 2 - $"$Integrating with existing services$"$:
 		\begin{itemize}
-			\item Sport-Community with Tracking (Runtastic, RunKeeper, etc.)
-			\item other Sporttracking-Services (Pedometer, etc.)
+			\item Sport-Community with Tracking (e.g. Runtastic, Runkeeper, Nike Plus, ...)
+			\item Other health-related tracking services (e.g. Pedometer, Weighttracking, ...)
+			\item Health-related gaming platforms (e.g. Geocaching, ...)
 		\end{itemize}
-	\item Phase 3 - $"$Health Organisations$"$:
+	\item Phase 3 - $"$A new form of health-care system$"$:
 		\begin{itemize}
@@
 
-When a user buys something in a shop of a partner he can register the product within an app. In the system the purchases get anonymised, saved and analyzed based on a transparent score-schema. \\
-
-The user can exchange the scores for gifts like coupons for healthy shopping at a partners store.
-Moreover the platform can be used for rankings (which of the user lives most healthy?) and lotteries.
-Partners are able to interact with the user over the platform.
-So they can advertise new promotions.
-This promotion can be used by the user for getting additional scores.
+When a user buys something in a partner shop the product gets registered at our platform.
+The system stores the information in an anonymised form and calcualates statistics based on a transparent score-schema.
+The user can then exchange his earned points for gifts like coupons for healthy shopping at a partner's store.
+Moreover the platform generates a monthly, opt-in ranking of people living in a specific area, people who register them as a group of friends or all registered people as a whole.
+It therefore aims at answering questions like $"$which user lives most healthy?$"$, $"$which user eats most healthy?$"$, $"$which user walks the farthest distance in a day?$"$ and similar.
+Partners are able to interact with the user with the use of the platform so they can selectively advertise new products of interest for the user.
 \\
@@
 \begin{itemize}
-\item \textbf{Health of the user}: People are getting more sensible for health-care.
+\item \textbf{Improving overall health of the user}: People are getting more sensible for health-care.
 So they get forced to live in a healthier way.
@@
 So the whole government will have a benefit from this platform and more healthier people.
+\item \textbf{Financial benefits for the user}: Users will be given discounts and coupon codes when buying healthy products at partner stores. 
 \item \textbf{Advertisement for the partners}: For the partners the platform offers a chance to advertise their promotions.
@@
 One possible effect is a gain in customer loyalty.
-The customer is getting animated to buy more at partners stores.
-Therefore partners have to refinance a part of the platform.
-\item \textbf{Benefits for users}: Users should be given discounts when they buy some healthy things at partners stores.
-This could be achieved by giving coupons to users from a lottery in the platform.
 

### 2012-11-11 paper/mswp2012-proposal.tex
added Pagebreak, just to make it pretty
introduction

@@
 The partners mainly use our platform for advertisement and customer relationships, which brings benefits to them as well.
-\\
+
+\pagebreak
 
@@
 
-\note{
-\begin{itemize}
-	\item {\em Length: 2-3 pages}
-	\item {\bf Why?}
-	\item Introduction
-	\item Context
-	\item What is the current situation?
-	\item What is the open/unresolved problem or opportunity?
-	\item Why is it a problem?
-	\item What is unknown?
-	\item What could be improved?
-	\item Explanation of fundamental terms and basic definitions.
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%	\item {\em Length: 2-3 pages}
+%	\item {\bf Why?}
+%	\item Introduction
+%	\item Context
+%	\item What is the current situation?
+%	\item What is the open/unresolved problem or opportunity?
+%	\item Why is it a problem?
+%	\item What is unknown?
+%	\item What could be improved?
+%	\item Explanation of fundamental terms and basic definitions.
+%\end{itemize}
+%}
 
+More and more people are getting obese.
+They live unhealthy and do to less sport.
+Many health-reports in Europe and America describe the problem and show how fast the people are getting fat.
+Particular bad are the children, which also gets unhealthy.
+And these children are going to become serious problems when they are grown up.
+\\
+
+Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays.
+These people don’t only look bad.
+They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.
+\\
+
+In near future this will cause a lot of financial claim in our health-care-system.
+More and more people have to get treated in a hospital because of health problems caused by being obese over the years.
+\\
+
+The only way we can reduce this costs in future, is to live nowadays healthier.
+And for this the software system should help.
+If people can get an bonus for living healthier, they will get motivated to do so.
+They will use the system in their live and reduce the risks to get one of the illnesses caused by obese.
+\\
+
+Every single person has a benefit when he uses the system. So he can live longer and healthier. We can say: \\
+Mens sana in corpore sano \\
+This Latin slogan means: In a healthier body is a healthier soul. People will feel happier, if they live healthier.  \\
+
+Unfortunately it is not easy to motivate people to look on their own bodies.
+Many people are lazy and lay on the couch instead of going out for a walk.
+They buy junk food instead of fruits.
+Because they know how junk food tastes better.
+With this software system, the people should learn and accept a healthier way of living.
+They get a little benefit, when they buy an healthier fruit instead of junk food.
+\\
+
+These small benefits are combined in a challenge with all the other users of the system.
+So the motivation gets to a competition with a lot of other people living in a particular similar situation.
+\\
+
+Over all the health-care-system will lower the costs and so they can combine this system with their insurance-system.
+So people would have to use it for getting a cheaper insurance.
+So somebody who wants to live healthier can have a cheaper insurance.
+\\
+
+This project is accompanied by a scientific study.
+This study have to monitor the evolution of the health of the people while the use the system.
+This study show how efficient the system works.
+The iterative development of the system uses the data from the study for improving the output and to get healthier people.
+\\
+
+So everyone has a benefit with this system. The people are living healthier, happier and longer.  \\
 % --------------------------------------------------------------

### 2012-11-13 paper/mswp2012-proposal.tex
paar änderungen an indroduction

@@
 They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.
+\\
+
+In the Forbes List for the fattest nation, Austria is on place 52 with a fat rate of 57.1\%.\footnote{\url{forbes list: http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}.
+The Image on this site show the percentage of obese people in the European Union for male and femals.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=1\textwidth]{images/introduction/1.jpg}
+	\caption{Obese in the EU}
+	\label{fig:obese_in_eu_pdf}
+\end{figure}
+
+Unfortunately this trend starts early.
+The parents live unhealthy and show their children this unhealthy way of live.
+The children are overweight in young ages.
+And this can raise the impact on the life of the child when it is grown up.
+\\
+
+You can't teach an old dog new tricks.
+So the children are grown up without any real chance to live in a healthier way.
+But this slogan is not true at all.
+It is never too late for change something.
+But it gets more difficult.
 \\

### 2012-11-15 paper/mswp2012-proposal.tex
updated Glossar and moved Footnote to Bib

--- 2012-11-11 paper/mswp2012-proposal.tex
@@
 
-Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays.
+Studies \citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
 These people don’t only look bad.
@@
   \item[WP] Work Package
+  \item[OECD] Organisation for Economic Co-operation and Development
+  \item[RKI] Robert Koch Institut
  \end{description}

### 2012-11-15 paper/mswp2012-proposal.tex
added chapter gamification of healthcare

@@
 \setlength{\textheight}{243.119mm} % 297mm-40mm-10mm-(11pt=3.881mm)=
-\setlength{\oddsidemargin}{-0.4mm} % (1in=25.4mm)-0.4mm=25mm
+\setlength{\oddsidemargin}{-0.4mm} % (1in=25.4mm)-0.4mm=25mm<
 \setlength{\textwidth}{160mm} % 210mm-50mm=160mm
@@
 % --------------------------------------------------------------
+\pagebreak
 \section{State of the art / current knowledge}
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 2-5 pages}
-\item What results and approaches have already been presented in this or related areas?
-\item Relation to the international scientific work in the field (international status of the research)
-\item Description and critical discussion of related scientific work
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 2-5 pages}
+%\item What results and approaches have already been presented in this or related areas?
+%\item Relation to the international scientific work in the field (international status of the research)
+%\item Description and critical discussion of related scientific work
+%\end{itemize}
+%}
+
+\subsection{Gamification of Healthcare}
+Nowadays there are several products that are using a gamification approach to motivate the user-base to do sport-activities.
+
+\subsubsection{Nintendo Wii}
+
+One of the first well-known of these systems was introduced by the japanese company called Nintendo in the year 2005 and named Nintendo Wii.
+This product is a typical games consol, but offered a new kind of remote called ``Wii Remote''.
+The shape of this remote is also highly inspired by the form of an TV remote and uses 4 infrared sensors on top of this remote which makes it possible to point on several objects presented on the TV-screen with a precision compareable to a common mouse used for personal computers.
+\\
+
+The included accelerometer is the most important part of this remote which recognizes motions and rotations of the remote and lets users play their games in a very funny and highly interactive way. \\
+
+Another additional input device for the Nintendo Wii is called ``Wii Balance Board'' (see \ref{fig:wiiboard}), which users have to place on the floor in front of the games console.
+The users have to stand right on top of this board and are able to control the game by switching their weight from one side to the other side.
+For user feedback they also included speakers and vibration sensors into the Wii Remote. \\
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=12cm]{images/stateoftheart/wiiboard.jpg}
+\caption{Wii Balance Board in action}
+\label{fig:wiiboard}
+\end{center}
+\end{figure}
+
+All these devices are connected via Bluetooth with the Console and are heavy used by sport and fitness games.
+Some rehabiliation center are using these consoles to gamify the process and making workouts more interesting.
+These rehabilitation centers were also observed and analyzed in medical studies showing, that patients have more fun doing their daily workout and training and also getting back to a normal physical condition more quickly.
+\\
+
+\subsubsection{Xbox 360 and Kinect}
+Microsoft also introduced an additional remote for their Xbox 360 in the year 2010 called ``Kinect''.
+Kinect is working with a different Approach than Wii Remote.
+It's like a camera placed in front of the TV capturing the users and working with 3D motion sensor, facial recognition and voice recognition (see \ref{fig:kinect}).
+These facts lead to one big advantage compared to Nintendos remote: the user do not have to hald a remote in his hand and therefore the user isn't constrained within his motions and movements.
+\\
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=11cm]{images/stateoftheart/kinect.png}
+\caption{Microsofts Kinect remote}
+\label{fig:kinect}
+\end{center}
+\end{figure}
+
+Microsoft also offers a SDK and Developement ToolKit to allow programmers to build their own Kinect games or application.
+One of these experiements was build at the University of Minnesota and its goal was to measure or detect diseases like autism.
+It's also possible to connect a Kinect remote to a Windows PC which makes it easier to run such applications used in an scientific area.
+
+\subsubsection{Playstations Remotes Eye and Move}
+Sony also introduced in the year 2007 and 2009 two remotes, very similar to the previous described remtoes from Microsoft and Nintendo.
+
+Playstation Eye is very similar to Xbox Kinect, offering a camera and microphone to capture the users motions and voice.
+Playstation Move is an Wii Remote like remote with an additonal orb which can change the color to give additonal feedback to the user and is used as anchor point for the Playsstation Eye to recognize the movements.
+(see \ref{fig:playstationeyeandmove})
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=11cm]{images/stateoftheart/playstationeyeandmove.png}
+\caption{Playstation Move and Playstation Eye}
+\label{fig:playstationeyeandmove}
+\end{center}
+\end{figure}
 
 % --------------------------------------------------------------
+\pagebreak
 \section{Method}

### 2012-11-15 paper/mswp2012-proposal.tex
Introduction - now in English ;)

--- 2012-11-15 paper/mswp2012-proposal.tex
@@
 
-More and more people are getting obese.
-They live unhealthy and do to less sport.
-Many health-reports in Europe and America describe the problem and show how fast the people are getting fat.
-Particular bad are the children, which also gets unhealthy.
-And these children are going to become serious problems when they are grown up.
+Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercisement, especially in the so called western society.
+Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight.
+The biggest problem being the situation getting worse and worse - especially children are rapidly becoming a big part of the problem, the risk of being overweight is about 30 percent\footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
 \\
 
-Studies \citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
-These people don’t only look bad.
-They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.
+Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays.
+Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.
 \\
 
-In near future this will cause a lot of financial claim in our health-care-system.
-More and more people have to get treated in a hospital because of health problems caused by being obese over the years.
+In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}.
+Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=1\textwidth]{images/introduction/1.jpg}
+	\caption{Obese in the EU}
+	\label{fig:obese_in_eu_pdf}
+\end{figure}
+
+One reason for the negative trend of childhood overweight are bad role models.
+Parents living an unhealthy lifestyle affect and influence their children.
+A recent study suggests that at-risk children are identifyable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
+With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit.
+In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.
 \\
 
-The only way we can reduce this costs in future, is to live nowadays healthier.
-And for this the software system should help.
-If people can get an bonus for living healthier, they will get motivated to do so.
-They will use the system in their live and reduce the risks to get one of the illnesses caused by obese.
+The only way to stop this trend and to reduce the costs for health treatment is to live healthier today.
+This is the point where our modern health care system comes into play: We want to help people improving their lifestyle and staying fit by motivating them through the help of gamification and technology.
+Rankings against friends and neighbours as well as bonuses for reaching milestones are a vital part of our system.
+People shouldn't get forced to live healthy, they should do it self-motivated.
+We want to increase this motivation.
+This will eventually lead to a healthier society over time.
 \\
 
-Every single person has a benefit when he uses the system. So he can live longer and healthier. We can say: \\
-Mens sana in corpore sano \\
-This Latin slogan means: In a healthier body is a healthier soul. People will feel happier, if they live healthier.  \\
+Our goal is to make people realize how they can benefit from a healthier lifestyle. A latin quote goes as follows:
 
-Unfortunately it is not easy to motivate people to look on their own bodies.
-Many people are lazy and lay on the couch instead of going out for a walk.
-They buy junk food instead of fruits.
-Because they know how junk food tastes better.
-With this software system, the people should learn and accept a healthier way of living.
-They get a little benefit, when they buy an healthier fruit instead of junk food.
+\begin{center}
+	\emph{"Mens sana in corpore sano"}
+\end{center}
+
+A sound mind in a healthy body, people that are healthy feel happier.
+Unfortunately it is way harder to motivate people to look after themselves than it should be.
+One's weaker self is often blamed for becoming a so called modern couch potato.
+Combined with the increasing stress of today's achievement-oriented society this leads to long working hours without time for healthy meals or exercises.
+Most people ignore the fact that often small changes of their habits can lead to a healthier lifestyle without having to invest hours a day for doing sports.
+Taking the stairs instead of the elevator, using a standing desk instead of sitting in front of the computer all day long, taking the bike to work, buying fruits and healthy meals instead of chunkfood - all these things can dramatically improve your fitness and can be easily integrated as your day-to-day routines.
+What's missing?
+The motivation to do so.
+People are easy to influence (in a good sense).
+People are driven by results they can see and by competing with people they know.
+People want to be better than others, naturally.
+People enjoy being rewarded for their efforts.
+We want to use these inner forces and turn them into something good, we want to use them to help people improve their lifes.
 \\
 
-These small benefits are combined in a challenge with all the other users of the system.
-So the motivation gets to a competition with a lot of other people living in a particular similar situation.
-\\
-
-Over all the health-care-system will lower the costs and so they can combine this system with their insurance-system.
-So people would have to use it for getting a cheaper insurance.
-So somebody who wants to live healthier can have a cheaper insurance.
+Overall our modern health care system should lead to lowered costs for health care in general and it might be possible to integrate the system with private insurance systems.
+People would see another benefit of living healthy: cheaper insurance.
+People like to save money.
 \\
@@
 This project is accompanied by a scientific study.
-This study have to monitor the evolution of the health of the people while the use the system.
-This study show how efficient the system works.
-The iterative development of the system uses the data from the study for improving the output and to get healthier people.
+The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system, and how to improve these interactions.
+This data should lead to a good basis for future work on the topic.
 \\
-
-So everyone has a benefit with this system. The people are living healthier, happier and longer.  \\
 % --------------------------------------------------------------
@@
   \item[WP] Work Package
-  \item[OECD] Organisation for Economic Co-operation and Development
-  \item[RKI] Robert Koch Institut
  \end{description}

### 2012-11-15 paper/mswp2012-proposal.tex

@@
 
-Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays.
+Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
 Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.

### 2012-11-15 paper/mswp2012-proposal.tex
Start with goal and research questions

@@
 
-\providecommand*{\ShortTitle}{Modern voluntary Health-Care-System}
+\providecommand*{\ShortTitle}{Modern voluntary Health Care System}
 \providecommand*{\FullTitle}{The influence of gamification on the willingness to live healthy}
@@
 So they get forced to live in a healthier way.
-The healthcare-system is very expensive.
-So the whole government will have a benefit from this platform and more healthier people.
+Our health care system is very expensive.
+The whole government should have a benefit from this platform and more healthy people.
 \item \textbf{Financial benefits for the user}: Users will be given discounts and coupon codes when buying healthy products at partner stores. 
@@
 
-\note{
+%\note{
+%\begin{itemize}
+%	\item {\em Length: 1-2 pages}
+%	\item What is the goal of the project?
+%	\item Research questions
+%	\begin{itemize}
+%		\item 	    What are the hypotheses that are to be investigated?
+%		\item 	    Main hypothesis \& sub hypotheses
+%	\end{itemize}
+%	\item Which results should be achieved with the project?
+%	\begin{itemize}
+%	    	\item 	   What will be known afterwards that is not known now?
+%		\item	    What will be created that does not exist now?
+%	\end{itemize}
+%	\item Non-goals (What will not be part of the project? What will not be done?)
+%\end{itemize}
+%}
+
+The goal of the modern health care system is to create a new form of voluntary system that motivates people to live and stay healthy. 
+It is based on several pillars:
+
 \begin{itemize}
-	\item {\em Length: 1-2 pages}
-	\item What is the goal of the project?
-	\item Research questions
+	\item \emph{Technology}. 
+	The goal of the modern health care system is to use today's possibilities to support a healthier lifestyle.
+	\item \emph{Ubiqitous Computing and Usability}.
+	The modern health care system should be an easy to use system that transparently integrates into ones living day while staying out of the way and minimizing the need of manual interactions.
+	\item \emph{Psychology}.
+	The modern health care system should use and gather knowledge on what motivates people to stay in shape, especially in the field of gamification.
+\end{itemize}
+
+There are several research questions to be investigated:
 \begin{itemize}
-		\item 	    What are the hypotheses that are to be investigated?
-		\item 	    Main hypothesis \& sub hypotheses
+	\item How can tracking be automized and done transparently without the need of manual interaction?
+	\item How does gamification of day-to-day tasks affect people‘s motivation?
+	\item How can ubiqitous computing be used to support improving our health?
+	\item How can different ecosystems be integrated into one giant, interconnected system without sacrifying security and privacy?
 \end{itemize}
-	\item Which results should be achieved with the project?
-	\begin{itemize}
-	    	\item 	   What will be known afterwards that is not known now?
-		\item	    What will be created that does not exist now?
-	\end{itemize}
-	\item Non-goals (What will not be part of the project? What will not be done?)
-\end{itemize}
-}
 

### 2012-11-15 paper/mswp2012-proposal.tex
finished first draft of State of the Art

--- 2012-11-15 paper/mswp2012-proposal.tex
@@
 		\begin{itemize}
-			\item Sport-Community with Tracking (e.g. Runtastic, Runkeeper, Nike Plus, ...)
+			\item Sport-Community with Tracking (e.g. Runtastic, RunKeeper, Nike Plus, ...)
 			\item Other health-related tracking services (e.g. Pedometer, Weighttracking, ...)
@@
 
-Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercisement, especially in the so called western society.
-Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight.
-The biggest problem being the situation getting worse and worse - especially children are rapidly becoming a big part of the problem, the risk of being overweight is about 30 percent\footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
+More and more people are getting obese.
+They live unhealthy and do to less sport.
+Many health-reports in Europe and America describe the problem and show how fast the people are getting fat.
+Particular bad are the children, which also gets unhealthy.
+And these children are going to become serious problems when they are grown up.
 \\
 
-Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
-Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.
+Studies \citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
+These people don’t only look bad.
+They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.
 \\
 
-In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}.
-Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.
+In the Forbes List for the fattest nation, Austria is on place 52 with a fat rate of 57.1\%.\footnote{\url{forbes list: http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}.
+The Image on this site show the percentage of obese people in the European Union for male and femals.
 
@@
 
-One reason for the negative trend of childhood overweight are bad role models.
-Parents living an unhealthy lifestyle affect and influence their children.
-A recent study suggests that at-risk children are identifyable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
-With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit.
-In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.
+Unfortunately this trend starts early.
+The parents live unhealthy and show their children this unhealthy way of live.
+The children are overweight in young ages.
+And this can raise the impact on the life of the child when it is grown up.
 \\
 
-The only way to stop this trend and to reduce the costs for health treatment is to live healthier today.
-This is the point where our modern health care system comes into play: We want to help people improving their lifestyle and staying fit by motivating them through the help of gamification and technology.
-Rankings against friends and neighbours as well as bonuses for reaching milestones are a vital part of our system.
-People shouldn't get forced to live healthy, they should do it self-motivated.
-We want to increase this motivation.
-This will eventually lead to a healthier society over time.
+You can't teach an old dog new tricks.
+So the children are grown up without any real chance to live in a healthier way.
+But this slogan is not true at all.
+It is never too late for change something.
+But it gets more difficult.
 \\
 
-Our goal is to make people realize how they can benefit from a healthier lifestyle. A latin quote goes as follows:
-
-\begin{center}
-	\emph{"Mens sana in corpore sano"}
-\end{center}
-
-A sound mind in a healthy body, people that are healthy feel happier.
-Unfortunately it is way harder to motivate people to look after themselves than it should be.
-One's weaker self is often blamed for becoming a so called modern couch potato.
-Combined with the increasing stress of today's achievement-oriented society this leads to long working hours without time for healthy meals or exercises.
-Most people ignore the fact that often small changes of their habits can lead to a healthier lifestyle without having to invest hours a day for doing sports.
-Taking the stairs instead of the elevator, using a standing desk instead of sitting in front of the computer all day long, taking the bike to work, buying fruits and healthy meals instead of chunkfood - all these things can dramatically improve your fitness and can be easily integrated as your day-to-day routines.
-What's missing?
-The motivation to do so.
-People are easy to influence (in a good sense).
-People are driven by results they can see and by competing with people they know.
-People want to be better than others, naturally.
-People enjoy being rewarded for their efforts.
-We want to use these inner forces and turn them into something good, we want to use them to help people improve their lifes.
+In near future this will cause a lot of financial claim in our health-care-system.
+More and more people have to get treated in a hospital because of health problems caused by being obese over the years.
 \\
 
-Overall our modern health care system should lead to lowered costs for health care in general and it might be possible to integrate the system with private insurance systems.
-People would see another benefit of living healthy: cheaper insurance.
-People like to save money.
+The only way we can reduce this costs in future, is to live nowadays healthier.
+And for this the software system should help.
+If people can get an bonus for living healthier, they will get motivated to do so.
+They will use the system in their live and reduce the risks to get one of the illnesses caused by obese.
+\\
+
+Every single person has a benefit when he uses the system. So he can live longer and healthier. We can say: \\
+Mens sana in corpore sano \\
+This Latin slogan means: In a healthier body is a healthier soul. People will feel happier, if they live healthier.  \\
+
+Unfortunately it is not easy to motivate people to look on their own bodies.
+Many people are lazy and lay on the couch instead of going out for a walk.
+They buy junk food instead of fruits.
+Because they know how junk food tastes better.
+With this software system, the people should learn and accept a healthier way of living.
+They get a little benefit, when they buy an healthier fruit instead of junk food.
+\\
+
+These small benefits are combined in a challenge with all the other users of the system.
+So the motivation gets to a competition with a lot of other people living in a particular similar situation.
+\\
+
+Over all the health-care-system will lower the costs and so they can combine this system with their insurance-system.
+So people would have to use it for getting a cheaper insurance.
+So somebody who wants to live healthier can have a cheaper insurance.
 \\
@@
 This project is accompanied by a scientific study.
-The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system, and how to improve these interactions.
-This data should lead to a good basis for future work on the topic.
+This study have to monitor the evolution of the health of the people while the use the system.
+This study show how efficient the system works.
+The iterative development of the system uses the data from the study for improving the output and to get healthier people.
 \\
+
+So everyone has a benefit with this system. The people are living healthier, happier and longer.  \\
 % --------------------------------------------------------------
@@
 
+Today there are several approaches to motivate people to live healthier, but most of them are just focusing on doing your regular workout and track your success or just help to have more fun doing physical activities.
+\\
+
+Analyzing these current systems you can find two strategies, on one hand the gamification of healthcare (see \ref{sect:star:gamification}) and on the other hand a combination of helathcare and social engineering with special plattforms.
+
 \subsection{Gamification of Healthcare}
+\label{sect:star:gamification}
 Nowadays there are several products that are using a gamification approach to motivate the user-base to do sport-activities.
+This technique is used in the gaming industry to sell sport and fitness games and was also part of creating new remotes and interaction possibilites to evolve the whole gaming industry.
 
 \subsubsection{Nintendo Wii}
-
+\label{sect:star:wii}
 One of the first well-known of these systems was introduced by the japanese company called Nintendo in the year 2005 and named Nintendo Wii.
@@
 \subsubsection{Xbox 360 and Kinect}
+\label{sect:star:kinect}
 Microsoft also introduced an additional remote for their Xbox 360 in the year 2010 called ``Kinect''.
@@
 \begin{center}
-\includegraphics[width=11cm]{images/stateoftheart/kinect.png}
+\includegraphics[width=12cm]{images/stateoftheart/kinect.png}
 \caption{Microsofts Kinect remote}
@@
 \subsubsection{Playstations Remotes Eye and Move}
+\label{sect:star:eyemove}
 Sony also introduced in the year 2007 and 2009 two remotes, very similar to the previous described remtoes from Microsoft and Nintendo.
@@
 \begin{center}
-\includegraphics[width=11cm]{images/stateoftheart/playstationeyeandmove.png}
+\includegraphics[width=12cm]{images/stateoftheart/playstationeyeandmove.png}
 \caption{Playstation Move and Playstation Eye}
@@
 \end{figure}
+
+\subsection{Socialisation of Healthcare}
+\label{sect:star:social}
+Another way of motivating people to live healthier and doing their regular workout is to add a social component to the expierence of making sport.
+The goal of this approach is to create a social network where you can track your own success and compare it to the progress of your friends.
+
+\pagebreak
+
+\subsubsection{Introducing RunKeeper}
+\label{sect:star:runkeeper}
+RunKeeper was created several years ago and started as a simple tracking plattform to track your runs.
+It works with several smartphones and uses their GPS sensor to track speed, distance, elevation and other things of a run.
+
+In addition they build a website where you can see your previous runs on a map and give you overview of your last activities with monthly stats (see \ref{fig:runkeeper}).
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=12cm]{images/stateoftheart/runkeeper.jpg}
+\caption{RunKeeper website and mobile clients}
+\label{fig:runkeeper}
+\end{center}
+\end{figure}
+
+\paragraph{Social aspects:} The next step was to add social features to their plattforms to make this service more intersting for their users.
+They introduced a route-sharing feature, which makes it possible to find interesting routes near you posted by other runners.
+To get in contact with these people they introduced the so called Street Team to see the activities from your friends and match against each other, a simple way to gamify your daily workout.
+
+\paragraph{Enhance the plattform:} RunKeeper also introduces some other features to motivate the users even more to do their workout.
+One of these was the ability to set goals on a monthly based, like total distance or furthest run, etc.
+\\
+
+They also thought how to make this plattform a little bit more profitable and released a new way to manage your training with this plattform, called ``Training Plans''.
+You can subscribe to these plans after paying a small fee and attend a class.
+The plans are created from professional trainers and have different goals, e.g.
+complete a 10 kilometres run within 50 minutes.
+The users track their run to the classes and are allowed and welcome to spread their success within the class with their classmates.
+
+\paragraph{The look over the rim of a tea cup:} RunKeeper tried to expand their offer to cover more bases.
+First step was to include more different sports to allow cycler or swimmer to track their activities too.
+\\
+
+Offering sport equipment to track your heart rate or your body weight and body fat were another steps in this direction to track more mesaurement parameter to observe the users health status. \\
+
+In their blog they are spreading really nice success stories about people losing a lot of weight because of the motivitaion they got from RunKeepers apps, plattform and equipement. \\
+
+HealthGraph is another plattform they are hosting which focuses more on the social aspects and this system is covering even more health parameter than the original RunKeeper website, but this plattform is still in kind of a beta mode.
+
+To catch even more ideas and possibilites they also released an SDK to integrate RunKeeper into other apps and allow other plattform to use these collected data. \\
+
+\subsubsection{Similar Plattforms}
+\label{sect:star:competitors}
+There are several other plattforms tracking your sport activities, a lot of them do not offer that many features as RunKeeper does, do not have that many users, or do not follow such an intense social approach.
+
+\begin{itemize}
+	\item \textbf{Runtastic:} This is a very similar system like RunKeeper but also had a lot of success during the last few years.
+The company is situated in Linz in Austria and expanded their user based all over the world.
+A lot of people switched from RunKeeper to Runtastic because of several individual reasons (e.g.
+design, user-base, etc.).
+\\
+	\item \textbf{Nike+:} Nike also startet with a tracking service for runners, but they used another sport equipment to track the distance of your run.
+The user had to place these small sensor on one of his shoes and this sensore tracked your step like a step counter and calculated your run distance.
+
+	They also began to work on an app and introduce new features and also selling their combined sport equpements like gears and so on.
+Also the social aspect became more and more important in their system.
+
+	One big advantage is the use of Xboxs Kinect which not only combine these two plattforms but also combine the two strategies of gamification and socialisation. \\
+	\item \textbf{Other plattforms introduced by several sport equipment manufactors:} Other manufactors like Polar also introduced their own plattforms but have problems to reach a big user-base.
+They tried to jump on this movement made by plattforms like RunKeeper or Runtastic, but couldn't get that much success with their systems, although they have a lot of success with their equipment.
+\end{itemize}
 

### 2012-11-17 paper/mswp2012-proposal.tex
added 4. 3 of 5 questions

@@
 }
+\subsection{Scientifical point of view}
+
+The approach to create a game out of tasks for sick people is not new.
+Dealing with traumatized children by example is nowadays often combined with a game.
+There are several different developments of games to fit the needs of different patients and problem fields.
+Furthermore there are very successful social gamifications like "Foursquare" \footnote{\url{https://foursquare.com/about/}} where people check in to places and earn achievements.
+All of that to keep track of what friends are doing.
+There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations.
+For example a hospital can keep track of their patients health status after surgeries or treatments remote.
+A good idea would be to use the gathered data for better observation of diabetics.
+Hardware to gather the additional data is already available (see \footnote{\url{http://www.bgstar.com/web/ibgstar}}).
+These possibilities to collect data lead to more knowledge of different diseases and effectiveness of treatments.
+By example collection the data of stuff people eat and how much they do physical workouts combined with the actual disease can help creating specialized therapies and new approaches to improve existing ones.\\
+
+\subsection{Open questions}
+There are many studies about the influence of games in everyday life.
+Some scientists (see Jane McGonigal) are trying to use games to let people learn to get the most out of their lifes.
+Her experiments show that habits changed during playing a game with real world content like a global lack of oil are kept by most of the players even after ending the game.
+These experiments were made with small groups of 500 to 1700 people as a sort of proof of concept.
+No one knows what impact it may have when millions of people are achieving a healthier life through various gaming strategies and what comes out of the motivation they put into it.
+So many questions in the area of wide field gamification are still not answerable.
+
+\subsection{Innovative apsects}
+The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new.
+In Africa there is a project to do a basic doctor consultation by SMS.
+The reason for this is because nothing is spread that widely other than a simple mobile phone.
+Going many kilometers for a checkup to the next doctor is often way to far for people with no car or the possibility to use public transportation.
+Approaches like this one are already rolled out for certain diseases and specialized groups (see \footnote{\url{http://derstandard.at/1345166647163/Der-Doktor-im-iPhone}}).
+Combining all the existing programs to one big socialized game for healthier living could even change economy.
 

### 2012-11-19 paper/mswp2012-proposal.tex
kommentare entfernt - pdf neu erzeugt - fürs zeigen beim tut

@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 1-2 pages}
-\item Why is the project scientifically interesting?
-\item Did others point out that this is an open question?
-\item What are the innovative aspects that make it interesting?
-\item How could the project break new ground scientifically?
-\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 1-2 pages}
+%\item Why is the project scientifically interesting?
+%\item Did others point out that this is an open question?
+%\item What are the innovative aspects that make it interesting?
+%\item How could the project break new ground scientifically?
+%\item To what extent are the objectives ambitious and beyond the state of the art (e.g. novel concepts and approaches or development across disciplines)?
+%\end{itemize}
+%}
 \subsection{Scientifical point of view}
@@
 % --------------------------------------------------------------
-\pagebreak
+%\pagebreak
 \section{State of the art / current knowledge}

### 2012-11-22 paper/mswp2012-proposal.tex
Try to answer more questions of 'Project goals and deliverables'

@@
 	The goal of the modern health care system is to use today's possibilities to support a healthier lifestyle.
+Technology is often blamed as a culprit for the increasing number of unhealthy people.
+We want to use technology to increase the overall health of people.
+Currently there are several focused approaches that use technology to improve health, see \ref{sect:star}.
+We want to create a system that does not only track isolated parts of your health-related activities but rather creates a big picture of everything you do and therefore is much more accurate than the existing systems.
 	\item \emph{Ubiqitous Computing and Usability}.
 	The modern health care system should be an easy to use system that transparently integrates into ones living day while staying out of the way and minimizing the need of manual interactions.
+The increasing success of mobile computing was a start to a new form of computing ultimately leading to ubiquitous and pervasive computing in the future.
+Ubiquitous computing is a post-desktop model of human computer interaction and describes the integration of computing into everydays activities.
+The modern health care system should be a case study on how ubiquitous computing performs on a broader range.
 	\item \emph{Psychology}.
 	The modern health care system should use and gather knowledge on what motivates people to stay in shape, especially in the field of gamification.
+The broad range of data generated by our system should be analyzed and evaluated to generate statistics on how gamification of everydays tasks can improve life.
+The game designer Jane McGonigal describes her journey from becoming suicidal to enjoying life in her TED talk \emph{The game that can give you 10 extra years of life} \footnote{\url{http://www.ted.com/talks/jane_mcgonigal_the_game_that_can_give_you_10_extra_years_of_life.html}}.
+She describes how turning her life into a game changed her perception of life and made her a happy person.
+This and other examples clearly show that gaming can have a very high impact on peoples life, with the help of the modern health care system we want to generate scientific data to prove this.
+	\item \emph{Security and Privacy}.
+	The increasing trend to an interconnected system and to ubiquitous and pervasive computing leads to higher risks of misuse of data.
+Health related data is very sensible data and therfore the modern health care system must guarantee data security and privacy from today's point of view.
+We need to investigate in how communication can stay private and how data can be obsfuscated without loosing the ability to generate useful statistics.
 \end{itemize}
@@
 \end{itemize}
+
+The main hyphotesis to be investigated in this project is in the field of usability and ubiquitous computing.
+We want to generate knowledge on how a tracking system that monitors your whole day can be designed without being noticable and annoying.
+As already stated such a system can only succeed if the generation of useful data is as automized as possible, manual entries of exercices or nutrition facts can improve the data accuracy but shouldn't be vital for a working system.
+
+The focus of the modern health care system isn't to become a game and therefore to compete with other game approaches like XBox Kinect or the Nintendo Wii.
+The main goal of these devices is to be a gaming platform, exercising while playing is a secondary factor that is to a great extent used for marketing reasons.
+Furthermore the modern health care system is no phychological study.
+The knowledge generated in this area is a side-product and not the main focus and the evaluation of the generated data is not part of the project.
+We also do not want to create an advertisement platform that can be (ab)used by our partners to spam our users.
+We do offer targeted ads, but only to a certain extend to be able to gain the interest of more partners in the industry.
 
@@
 
-\subsection{Innovative apsects}
+\subsection{Innovative aspects}
 The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new.

### 2012-11-22 paper/mswp2012-proposal.tex
Fixing some typos and notes from the tutor

@@
 
-Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercisement, especially in the so called western society.
+Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society.
 Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight.
-The biggest problem being the situation getting worse and worse - especially children are rapidly becoming a big part of the problem, the risk of being overweight is about 30 percent\footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
+The biggest problem in this area is that the situation is getting worse and worse.
+Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child is about 30 percent, according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
 \\
@@
 Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
-Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.
+Being overweight affects your life in a lot of ways.
+From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \ref{carr05}.
+Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.
 \\
@@
 Parents living an unhealthy lifestyle affect and influence their children.
-A recent study suggests that at-risk children are identifyable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
+A recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
 With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit.

### 2012-11-22 paper/mswp2012-proposal.tex
Fixing references

@@
 
-Studies\citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays.
+Studies\citep{rki2012} show, that about 23 Percent of the people in Germany are obese nowadays.
 Being overweight affects your life in a lot of ways.
-From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \ref{carr05}.
+From today's point of view overweight people are less attractive than others, have less success and and are more likely to be the victims of day-to-day discrimination \citep{carr05}.
 Moreover obesity can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.
@@
 
-\bibliographystyle{apalike}
+\bibliographystyle{plainnat}
+\nocite{*}
+
 \bibliography{mswp2012-proposal}

### 2012-11-22 paper/mswp2012-proposal.tex
Trying to give the introduction a little bit more structure

@@
 The biggest problem in this area is that the situation is getting worse and worse.
-Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child is about 30 percent, according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
+Especially children are rapidly becoming a big part of the problem, the risk of being an overweight child in the US is about 30 percent - according to the Center for Disease Control \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
+Another recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
 \\
 
-Studies\citep{rki2012} show, that about 23 Percent of the people in Germany are obese nowadays.
+The situation in Europe isn't any better.
+European studies\citep{rki2012} show, that about 23 percent of the people living in Germany are obese nowadays.
+In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}.
+Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.
+
 Being overweight affects your life in a lot of ways.
@@
 \\
-
-In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}.
-Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.
 
@@
 Parents living an unhealthy lifestyle affect and influence their children.
-A recent study suggests that at-risk children are identifiable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}.
 With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit.
@@
 This project is accompanied by a scientific study.
-The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system, and how to improve these interactions.
+The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system and how to improve these interactions.
+The focus hereby is on the usability of an ubiquitous health tracking system that (half-)automatically generates useful data of the habits of the participants.
 This data should lead to a good basis for future work on the topic.
@@
 As already stated such a system can only succeed if the generation of useful data is as automized as possible, manual entries of exercices or nutrition facts can improve the data accuracy but shouldn't be vital for a working system.
+\\
 

### 2012-11-22 paper/mswp2012-proposal.tex
Starting to rewrite scientific relevance section

@@
 \\
+
 % --------------------------------------------------------------
@@
 %}
+
 \subsection{Scientifical point of view}
+Using gamification as a motivational factor isn‘t new, there are several systems and successful gamifications like $"Foursquare"$ \footnote{\url{https://foursquare.com/about/}} on the market.
+See \ref{sect:star} for a list of other systems using gamification in a health-related environment.
+The modern health care system is scientifically interesting because it combines several well-known approaches into a new interconnected system and it is unknown if and how such a system can work.
+There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations.
+The modern health care system is on the one hand a psychological study on how gamification of everydays tasks can influence peoples behaviour, on the other hand it tries to gather new knowledge in the field of ubiquitous computing, usability and security/privacy.
+There are several questions we try to answer, see \ref{sect:goals} for an exhaustive list.
 
-The approach to create a game out of tasks for sick people is not new.
-Dealing with traumatized children by example is nowadays often combined with a game.
-There are several different developments of games to fit the needs of different patients and problem fields.
-Furthermore there are very successful social gamifications like "Foursquare" \footnote{\url{https://foursquare.com/about/}} where people check in to places and earn achievements.
-All of that to keep track of what friends are doing.
-There is a high scientific potential in our idea because it combines many of already given approaches with existing infrastructure and organizations.
-For example a hospital can keep track of their patients health status after surgeries or treatments remote.
-A good idea would be to use the gathered data for better observation of diabetics.
-Hardware to gather the additional data is already available (see \footnote{\url{http://www.bgstar.com/web/ibgstar}}).
-These possibilities to collect data lead to more knowledge of different diseases and effectiveness of treatments.
-By example collection the data of stuff people eat and how much they do physical workouts combined with the actual disease can help creating specialized therapies and new approaches to improve existing ones.\\
+It is already known that gamification, achievements and rankings can boost people's motivation.
+The questions we try to answer are whether gamification of simple tasks can lead to a long-term improvement of peoples attitude towards health.
+By using several sources for tracking we can gather more data than any other system already on the market and can therefore generate much more accurate data that is needed to answer those questions.
+The term \emph{ubiquitous computing} was first mentioned by Mark Weiser in 1988 and was shaped in his paper \emph{The computer for the 21st century} \cite{weiser99}.
+Since then ubiquitous computing became a trending form of computing which we believe will play a more and more important role in the future.
+The modern health care system tries to make use of ubiquitous computing in a broad range and therefore tries to push the integration of computing in day-to-day tasks and this new form of human computer interaction.
+By using an integrated system for health tracking on such a broad range ubiquitous computing can be pushed to its limits, since we need to track data from several forms of sources and sensors and this from a statistically relevant number of people.
+\\
 

### 2012-11-22 paper/mswp2012-proposal.tex
I don't like latex citations

@@
 Using gamification as a motivational factor isn‘t new, there are several systems and successful gamifications like $"Foursquare"$ \footnote{\url{https://foursquare.com/about/}} on the market.
-See \ref{sect:star} for a list of other systems using gamification in a health-related environment.
+See section \ref{sect:star} for a list of other systems using gamification in a health-related environment.
 The modern health care system is scientifically interesting because it combines several well-known approaches into a new interconnected system and it is unknown if and how such a system can work.
@@
 The modern health care system is on the one hand a psychological study on how gamification of everydays tasks can influence peoples behaviour, on the other hand it tries to gather new knowledge in the field of ubiquitous computing, usability and security/privacy.
-There are several questions we try to answer, see \ref{sect:goals} for an exhaustive list.
+There are several questions we try to answer, see section \ref{sect:goals} for an exhaustive list.
+\\
 

### 2012-11-22 paper/mswp2012-proposal.tex
added Comparison between existing systems and our project/plattform

--- 2012-11-22 paper/mswp2012-proposal.tex
@@
 % --------------------------------------------------------------
+\pagebreak
+
 \section{Project goals and deliverables}
@@
 
+\pagebreak
+
+\subsection{Approach of this Project}
+This project does not follow the same approach as the above mentioned Social Plattforms or Game Consoles.
+
+Both mentioned approaches are combining their plattform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\
+
+The goal of this project is to make people live healthier using motivation hints and a huge fun factor combined with social aspect.
+All of the mentioned systems are using their methods to sell their products to get a financial benefit out of the project, unlike this project is focusing only on the healthiness of its users, which also means that this project is getting money out of other stakeholders, but not from its users directly.
+\\
+
+This facts also give the system the ability to focus more on the users needs than other systems and introduce more health-saving-features in the future.
+The goal should be to sell an attitude to life, but not a product such as remotes, consoles or sport articles.
+Because of these prerequisites its easier to convince scientific stakeholders like medical universities, hospitals, doctors etc.
+to participate in such a plattform.
+
 % --------------------------------------------------------------

### 2012-11-22 paper/mswp2012-proposal.tex

--- 2012-11-22 paper/mswp2012-proposal.tex
@@
 
+\pagebreak
+
 \subsection{Socialisation of Healthcare}
@@
 The goal of this approach is to create a social network where you can track your own success and compare it to the progress of your friends.
-
-\pagebreak
 
@@
 \end{itemize}
+
+\pagebreak
+
+\subsection{Approach of this Project}
+This project does not follow the same approach as the above mentioned Social Plattforms or Game Consoles.
+
+Both mentioned approaches are combining their plattform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\
+
+The goal of this project is to make people live healthier using motivation hints and a huge fun factor combined with social aspect.
+All of the mentioned systems are using their methods to sell their products to get a financial benefit out of the project, unlike this project is focusing only on the healthiness of its users, which also means that this project is getting money out of other stakeholders, but not from its users directly.
+\\
+
+This facts also give the system the ability to focus more on the users needs than other systems and introduce more health-saving-features in the future.
+The goal should be to sell an attitude to life, but not a product such as remotes, consoles or sport articles.
+Because of these prerequisites its easier to convince scientific stakeholders like medical universities, hospitals, doctors etc.
+to participate in such a plattform.
 

### 2012-11-22 paper/mswp2012-proposal.tex
Reworking open questions

--- 2012-11-22 paper/mswp2012-proposal.tex
@@
 \subsection{Open questions}
-There are many studies about the influence of games in everyday life.
-Some scientists (see Jane McGonigal) are trying to use games to let people learn to get the most out of their lifes.
-Her experiments show that habits changed during playing a game with real world content like a global lack of oil are kept by most of the players even after ending the game.
-These experiments were made with small groups of 500 to 1700 people as a sort of proof of concept.
-No one knows what impact it may have when millions of people are achieving a healthier life through various gaming strategies and what comes out of the motivation they put into it.
-So many questions in the area of wide field gamification are still not answerable.
+The game designer and scientist Jane McGonigal, once suffering from depression herself, investigates in several research projects and studies on how gamification can improve people's life and happiness \footnote{\url{http://janemcgonigal.com/learn-me/}}.
+For this purpose she once created a game SuperBetter to treat herself, leading to the founding of her company SuperBetter Labs.
+Her experiments show that habits learned during playing a game with real world content can influence people‘s behaviour even after the game already ended.
+The game \emph{World without Oil} \footnote{\url{http://worldwithoutoil.org/metaabout.htm}} is an alternate reality game to call attention to a possible future oil shortage.
+People playing this game showed to be more sensitive for sustainable oil usage afterwards.
+The open question we want to answer is whether gamification can have a similar impact on the long-term attitude of people towards living a healthy life.
+We want to find out which factors can lead to a success or a failure of this system and how different societies need different motivations factors.
+\\
+
+Another open question we want to answer is if and how different isolated systems can be interconnected in a useful way, and whether we can infer a general approach for such a task.
+One important point of the interconnected data mining is to not sacrify security and privacy, while still keeping the possibility to do useful evaluations and create meaningful statistics.
+There are several algorithms that can be used to do privacy-preserving data mining like Partitioning, Randomization, Group Based Anonymization or special algorithms for Distributed privacy-preserving data mining \citep{agrawal2000}.
+We need to reasearch which algorithms are most suitable for our needs.
 

### 2012-11-22 paper/mswp2012-proposal.tex
Some more open questions

@@
 
+Furthermore we want to investigate in the field of human computer interaction.
+We want to gather knowledge on how to improve the interaction between people and their mobile phones and several other pervasive computing systems they use throughout this study.
+Usability in the field of mobile and ubiquitous computing is still a very new scientific topic and we want to improve our knowledge about how to design systems that stay out of the way of the user.
+
 \subsection{Innovative aspects}

### 2012-11-22 paper/mswp2012-proposal.tex
innovative aspects (by gerhard), changes to state of the art as requested by tutor (by messi)

@@
 \subsection{Innovative aspects}
-The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new.
+%The combination of different aspects already in use like surveillance of old people living alone to achieving the daily goal of walking 1.5 kilometers or drinking 2.5 liters of water is new.
 In Africa there is a project to do a basic doctor consultation by SMS.
@@
 Combining all the existing programs to one big socialized game for healthier living could even change economy.
+
+As described in the sections above, there are many different standalone solutions/products in the area of technical-backed healthcare.
+Our study aims at investigating the possibility of combining them to a whole single system which would lead to a gain in additional value.
+For the resulting system that means, that the user should not be forced to download and install several different apps or helpers (s)he wants to use, but get provided with one single interface which allows to benefit from it at least as much as if every single application would have been used separately by the user.
+
+Another innovative aspect is the attempt to keep the user interface as much out of the way of the user as possible.
+User interface design could step at a new higher level, where less commands are necessary to get more information and benefit out of the system.
+We want to search for and present new ground-breaking methods in user interface design for use in ubiquitous software systems.
 
@@
 
+Games using these features are e.g. ``Yoga'', EA Sports ``Active 2'' or the game compilation ``Wii Sports''. \\
+
 \subsubsection{Xbox 360 and Kinect}
@@
 The goal of this approach is to create a social network where you can track your own success and compare it to the progress of your friends.
+This area combines knowledge from psychology, social studies and the corresponding behaviour of human beings reacting to such social structures like social networks.
 
@@
 \subsection{Approach of this Project}
-This project does not follow the same approach as the above mentioned Social Plattforms or Game Consoles.
+This project does not follow the same approach as the above mentioned Social Platforms or Game Consoles.
 
-Both mentioned approaches are combining their plattform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\
+Both mentioned approaches are combining their platform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\
 

### 2012-11-22 paper/mswp2012-proposal.tex
introduction quelle und 4. quelle

@@
 
-Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society.
+Recent studies \citep{euobes2003} show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercise, especially in the so called western society.
 Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight.
@@
 Her experiments show that habits learned during playing a game with real world content can influence people‘s behaviour even after the game already ended.
-The game \emph{World without Oil} \footnote{\url{http://worldwithoutoil.org/metaabout.htm}} is an alternate reality game to call attention to a possible future oil shortage.
+The game \emph{World without Oil} \citep{wwoil2007} is an alternate reality game to call attention to a possible future oil shortage.
 People playing this game showed to be more sensitive for sustainable oil usage afterwards.

### 2012-11-26 paper/mswp2012-proposal.tex
Just committing for gspot to pull
Start with UCD

@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 2-5 pages}
-\item {\bf How?}
-\item How should the expected results be achieved?
-\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
-\item Description of the methods.
-\item Justifications for chosen methods.
-\end{itemize}
-}
+\subsection{User Centered Design}
+We chose \emph{User Centered Design} as the procedure model used for the modern health care system.
+We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system.
+User Centered Design is an iterative process that aims at supporting this procedure by integrating the user into the design process.
+By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work.
+User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods to emphasize functionality and robustness of systems.
+User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:
+
+\begin{enumerate}
+	\item Research Phase
+	\item Design Phase
+	\item Prototyping Phase
+	\item Evaluation Phase
+\end{enumerate}
+
+\begin{figure}[htb]
+	\centering
+		\includegraphics[width=1\textwidth]{images/UCD.pdf}
+	\caption{User Centered Design}
+	\label{fig:UCD}
+\end{figure}
+
+% - Literaturrecherche - was gibt es bereits, was kann man wiederverwenden, was kann man besser machen?
+% - Umfragen bei Partnern - was wird benötigt + Auswertung der Empirie
+% - Usability-Tests, User-Tests
+% - SW-Entwicklungsmethoden??? Wasserfall - Prototyping - oder sonst was? Gehört das hier dazu?
+
+%\note{
+%\begin{itemize}
+%\item {\em Length: 2-5 pages}
+%\item {\bf How?}
+%\item How should the expected results be achieved?
+%\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
+%\item Description of the methods.
+%\item Justifications for chosen methods.
+%\end{itemize}
+%}
 

### 2012-11-26 paper/mswp2012-proposal.tex
method: prototyping, empirical study, research - notes in german added

--- 2012-11-22 paper/mswp2012-proposal.tex
@@
 There are several algorithms that can be used to do privacy-preserving data mining like Partitioning, Randomization, Group Based Anonymization or special algorithms for Distributed privacy-preserving data mining \citep{agrawal2000}.
-We need to reasearch which algorithms are most suitable for our needs.
+We need to research which algorithms are most suitable for our needs.
 
@@
 Nowadays there are several products that are using a gamification approach to motivate the user-base to do sport-activities.
-This technique is used in the gaming industry to sell sport and fitness games and was also part of creating new remotes and interaction possibilites to evolve the whole gaming industry.
+This technique is used in the gaming industry to sell sport and fitness games and was also part of creating new remotes and interaction possibilities to evolve the whole gaming industry.
 
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 2-5 pages}
-\item {\bf How?}
-\item How should the expected results be achieved?
-\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
-\item Description of the methods.
-\item Justifications for chosen methods.
-\end{itemize}
-}
+%Als Vorgehensmodell für dieses Projekt wurde das User Centered Design ausgewählt.
+Um ein effektives, interaktives System zu bauen müssen die Benutzer identifiziert und ihre Auf- gaben und Bedürfnisse studiert werden.
+User Centered Design ist ein iterativer Prozess, der dieses Vorhaben unterstützt und der im Wesentlichen folgende vier Phasen durchläuft[10]:
+%1. Analyse des Nutzungskontextes
+%2. Definition der Anforderungen
+%3. Konzeption und Entwurf/Prototyping 4. Evaluation
+%Im Rahmen dieser Arbeit sollen für das Projekt In-Kontakt die Phasen 1 bis 3 durchlaufen werden.
+
+\subsection{User Centered Design}
+We chose User Centered Design as the procedure model for the modern health care system.
+
+\begin{figure}[tb]
+	\centering
+		\includegraphics[width=1\textwidth]{images/UCD.pdf}
+	\caption{User Centered Design}
+	\label{fig:images_UCD}
+\end{figure}
+
+\subsection{Experimental Horizontal Prototyping}
+% Software-Entwicklungsmethode
+%Experimentelles Prototyping
+%Erstes Ergebnis: ein erster experimenteller Prototyp
+%Ziel: Sammeln von Erfahrungen mit dem Prototyp
+%Bei diesem Vorgehen wird zu Forschungszwecken bzw.
+zur Suche nach Möglichkeiten zur Realisierung ein experimenteller Prototyp entwickelt.
+An diesem wird anschließend eine sehr umfangreiche Problemanalyse und Systemspezifikation durchgeführt.
+Die gewonnenen Erkenntnisse können anschließend in einem richtigen Produkt verwertet werden.
+
+%Horizontales Prototyping [Bearbeiten]
+%Erstes Ergebnis: Eine ausgewählte Ebene des Gesamtsystems wird fertiggestellt.
+%Ziel: Eine funktionierende Ebene, die vorgestellt werden kann, oder an der sich andere Ebenen orientieren können.
+%In diesem Fall wird nur eine spezifische Ebene des Gesamtsystems realisiert, welche jedoch möglichst vollständig abgebildet wird.
+(z.B.
+Realisierung der GUI (Oberfläche) (ohne tiefer liegende Funktionalitäten), zur Vorlage für den Auftraggeber.) Diese Methode hat den Vorteil, dass man dem Auftraggeber schon etwas zeigen kann, ohne das komplette System entwickelt zu haben.
+Dies setzt jedoch eine starke (sowieso sinnvolle) Trennung der einzelnen Komponenten voraus.
+Die Oberfläche muss dementsprechend unabhängig von der dahinter liegenden Logik funktionieren oder wenn die Logik-Ebene umgesetzt wird, muss sie unabhängig von der Oberfläche funktionieren.
+
+%Vorteile [Bearbeiten]
+%Die Anforderungen der Anwender können laufend präzisiert und verifiziert werden. Damit sinkt das Risiko einer Fehlentwicklung.
+%Unbeabsichtigte Wechselwirkungen zwischen einzelnen Komponenten des Produkts können früher erkannt werden.
+%Der Fertigstellungsgrad ist besser verifizierbar.
+%Die Qualitätssicherung kann frühzeitig eingebunden werden.
+%Nachteile [Bearbeiten]
+%Prototyping verführt oft dazu, Anforderungen weder korrekt zu erheben noch sauber zu dokumentieren. Der Entwicklungsprozess kann sich dadurch erheblich verlangsamen.
+%Es entstehen während der Entwicklung zusätzliche Kosten, weil der Prototyp nur als Basis für die folgende eigentliche Entwicklung des Produktes dient.
+Diese Kosten und Zeitaufwand können durch weniger Nacharbeit am Endprodukt wieder ausgeglichen werden.
+
+% TODO Gerhard - Deutschen Text zusammenfassen und auf Englisch formulieren + Grafik für Prototyping
+
+\subsection{Empirical Study}
+
+% Getrennt nach Stakeholders - Partners, Users, (Governments extra oder zu Partners???)
+% Was wünschen sich die Partners?
+% Was wünschen sich die User? --> Verweis zu detaillierter Beschreibung in "User Centered Design"
+% - Umfragen bei Partnern - was wird benötigt + Auswertung der Empirie
+
+\subsection{Literature Research}
+% - Literaturrecherche - was gibt es bereits, was kann man wiederverwenden, was kann man besser machen?
+
+%\note{
+%\begin{itemize}
+%\item {\em Length: 2-5 pages}
+%\item {\bf How?}
+%\item How should the expected results be achieved?
+%\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
+%\item Description of the methods.
+%\item Justifications for chosen methods.
+%\end{itemize}
+%}
 

### 2012-11-26 paper/mswp2012-proposal.tex

@@
 
-%Als Vorgehensmodell für dieses Projekt wurde das User Centered Design ausgewählt.
-Um ein effektives, interaktives System zu bauen müssen die Benutzer identifiziert und ihre Auf- gaben und Bedürfnisse studiert werden.
-User Centered Design ist ein iterativer Prozess, der dieses Vorhaben unterstützt und der im Wesentlichen folgende vier Phasen durchläuft[10]:
-%1. Analyse des Nutzungskontextes
-%2. Definition der Anforderungen
-%3. Konzeption und Entwurf/Prototyping 4. Evaluation
-%Im Rahmen dieser Arbeit sollen für das Projekt In-Kontakt die Phasen 1 bis 3 durchlaufen werden.
+\subsection{User Centered Design}
+We chose \emph{User Centered Design} as the procedure model used for the modern health care system.
+We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system.
+User Centered Design is an iterative process that aims at supporting this procedure by integrating the user into the design process.
+By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work.
+User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods to emphasize functionality and robustness of systems.
+User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:
 
-\subsection{User Centered Design}
-We chose User Centered Design as the procedure model for the modern health care system.
+\begin{enumerate}
+	\item Research Phase
+	\item Design Phase
+	\item Prototyping Phase
+	\item Evaluation Phase
+\end{enumerate}
 
-\begin{figure}[tb]
+\begin{figure}[htb]
 	\centering
@@
 	\caption{User Centered Design}
-	\label{fig:images_UCD}
+	\label{fig:UCD}
 \end{figure}

### 2012-11-26 paper/mswp2012-proposal.tex
More information about UCD

@@
 \subsection{User Centered Design}
-We chose \emph{User Centered Design} as the procedure model used for the modern health care system.
+We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System.
 We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system.
-User Centered Design is an iterative process that aims at supporting this procedure by integrating the user into the design process.
+User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process.
 By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work.
-User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods to emphasize functionality and robustness of systems.
+User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system.
+\\
+
 User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:
@@
 		\includegraphics[width=1\textwidth]{images/UCD.pdf}
-	\caption{User Centered Design}
+	\caption{User Centered Design Process}
 	\label{fig:UCD}
 \end{figure}
+
+During the \emph{Research Phase} information about the users, their profiles and their needs is collected.
+During the \emph{Design Phase} the requirements are specified based on the information gathered in the research phase and the concepts are created.
+During the \emph{Prototyping Phase} various forms of mockups and prototypes are created based on the information gathered in the design phase.
+In the \emph{Evaluation Phase} the prototypes and mockups are finally discussed with the users and evaluated.
+It is important to repeatedly check if the needs of the users are still met.
+Therefore the phases are interconnected and fast iteration is a vital part of User Centered Design.
 

### 2012-11-26 paper/mswp2012-proposal.tex
described prototyping

@@
 \subsection{User Centered Design}
+\label{subsect:ucd}
 We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System.
@@
 \subsection{Experimental Horizontal Prototyping}
+We decided for a combination of experimental and horizontal prototyping as software development method.
+
+Experimental prototyping aims at creating a prototype of the system in an early phase of the development process and is therefore highly compatible with the use of user centered design (see \ref{subsect:ucd}).
+There is also a connection to the empirical study part (see \ref{subsect:emp_study}), as the prototype shall be used for evaluating requirements of users as well as of partners from the industry.
+Not only should an early prototype lead to a higher-sophisticated user interface with respect to ui design principles and usability issues, but also provide possibility to gain results for the research part of the overall project.
+
+The prototyping shall be executed in a horizontal manner, that means there should be a fully featured user interface before starting over with any kind of business logic implementation.
+The advantage of an horizontal approach is, similar to an experimental one, the perfect compatibility with user centered design.
+Of course this requires a strict separation of user interface and business logic implementation.
+
+One advantage of prototyping is, that potential errors in the user interface can be detected in an early phase of the project - also quality assurance can get embedded into the project as early as possible.
+
 % Software-Entwicklungsmethode
@@
 \subsection{Empirical Study}
+\label{subsect:emp_study}
 

### 2012-11-28 paper/mswp2012-proposal.tex
method: empirical study, literature research, new graphic in prototyping

@@
 	\centering
-		\includegraphics[width=1\textwidth]{images/UCD.pdf}
-	\caption{User Centered Design Process}
+		\includegraphics[width=0.8\textwidth]{images/method/UCD.pdf}
+	\caption{User Centered Design Process TODO MATTHIAS QUELLE ANGEBEN!}
 	\label{fig:UCD}
@@
 
-The prototyping shall be executed in a horizontal manner, that means there should be a fully featured user interface before starting over with any kind of business logic implementation.
+The prototyping shall be executed in a horizontal manner, that means there should be a fully designed user interface before starting over with any kind of business logic implementation.
+In contrast to that, vertical prototyping aims at implementing one specific feature from the frontend to the backend with its full functionality.
 The advantage of an horizontal approach is, similar to an experimental one, the perfect compatibility with user centered design.
 Of course this requires a strict separation of user interface and business logic implementation.
+See figure \ref{fig:prototyping} for a distinction between horizontal and vertical prototyping.
 
-One advantage of prototyping is, that potential errors in the user interface can be detected in an early phase of the project - also quality assurance can get embedded into the project as early as possible.
+\begin{figure}[htb]
+	\centering
+		\includegraphics[width=0.6\textwidth]{images/method/prototyping}
+	\caption{Horizontal and vertical prototyping \citep[Page 94]{DBLP:books/daglib/0076830}}
+	\label{fig:prototyping}
+\end{figure}
 
-% Software-Entwicklungsmethode
-%Experimentelles Prototyping
-%Erstes Ergebnis: ein erster experimenteller Prototyp
-%Ziel: Sammeln von Erfahrungen mit dem Prototyp
-%Bei diesem Vorgehen wird zu Forschungszwecken bzw.
-zur Suche nach Möglichkeiten zur Realisierung ein experimenteller Prototyp entwickelt.
-An diesem wird anschließend eine sehr umfangreiche Problemanalyse und Systemspezifikation durchgeführt.
-Die gewonnenen Erkenntnisse können anschließend in einem richtigen Produkt verwertet werden.
-
-%Horizontales Prototyping [Bearbeiten]
-%Erstes Ergebnis: Eine ausgewählte Ebene des Gesamtsystems wird fertiggestellt.
-%Ziel: Eine funktionierende Ebene, die vorgestellt werden kann, oder an der sich andere Ebenen orientieren können.
-%In diesem Fall wird nur eine spezifische Ebene des Gesamtsystems realisiert, welche jedoch möglichst vollständig abgebildet wird.
-(z.B.
-Realisierung der GUI (Oberfläche) (ohne tiefer liegende Funktionalitäten), zur Vorlage für den Auftraggeber.) Diese Methode hat den Vorteil, dass man dem Auftraggeber schon etwas zeigen kann, ohne das komplette System entwickelt zu haben.
-Dies setzt jedoch eine starke (sowieso sinnvolle) Trennung der einzelnen Komponenten voraus.
-Die Oberfläche muss dementsprechend unabhängig von der dahinter liegenden Logik funktionieren oder wenn die Logik-Ebene umgesetzt wird, muss sie unabhängig von der Oberfläche funktionieren.
-
-%Vorteile [Bearbeiten]
-%Die Anforderungen der Anwender können laufend präzisiert und verifiziert werden. Damit sinkt das Risiko einer Fehlentwicklung.
-%Unbeabsichtigte Wechselwirkungen zwischen einzelnen Komponenten des Produkts können früher erkannt werden.
-%Der Fertigstellungsgrad ist besser verifizierbar.
-%Die Qualitätssicherung kann frühzeitig eingebunden werden.
-%Nachteile [Bearbeiten]
-%Prototyping verführt oft dazu, Anforderungen weder korrekt zu erheben noch sauber zu dokumentieren. Der Entwicklungsprozess kann sich dadurch erheblich verlangsamen.
-%Es entstehen während der Entwicklung zusätzliche Kosten, weil der Prototyp nur als Basis für die folgende eigentliche Entwicklung des Produktes dient.
-Diese Kosten und Zeitaufwand können durch weniger Nacharbeit am Endprodukt wieder ausgeglichen werden.
-
-% TODO Gerhard - Deutschen Text zusammenfassen und auf Englisch formulieren + Grafik für Prototyping
+One advantage of prototyping is that potential errors in the user interface can be detected in an early phase of the project - also quality assurance can get embedded into the project as early as possible.
 
@@
 
-% Getrennt nach Stakeholders - Partners, Users, (Governments extra oder zu Partners???)
-% Was wünschen sich die Partners?
-% Was wünschen sich die User? --> Verweis zu detaillierter Beschreibung in "User Centered Design"
-% - Umfragen bei Partnern - was wird benötigt + Auswertung der Empirie
+Empirical study of the needs of the main stakeholders in the project is essential.
+By means of surveys and interviews we try to identify requirements and hope to get answers to the following (and more) questions:
+
+\begin{itemize}
+\item What do end users need/want? What is negligible and can therefore be omitted?
+\item What do they miss in actual systems?
+\item How do they wish to interact with the system?
+\item What are the needs of the different business partners?
+\item Which systems are currently in use at the partners processes?
+\item How would they improve their current systems?
+\end{itemize}
+
+Of course empirical study has to take place at a very early phase in the project to prevent undesirable development and ensure movement into the right direction from the very beginning.
+The contents of the questionnaire therefore have to be prepared conscientiously and meaningful, so that as much findings as possible can be deduced for use in later phases of the project.
 
 \subsection{Literature Research}
-% - Literaturrecherche - was gibt es bereits, was kann man wiederverwenden, was kann man besser machen?
+
+Certainly we to not have to reinvent the wheel.
+Therefore a detailed literature research has to be carried out to find possible approaches that can be reused.
+By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others projects.
+The literature research part aims at answering the following questions
+
+\begin{itemize}
+\item Which techniques are already in use or have been introduced in the field of
+\begin{itemize}
+\item healthcare applications?
+\item ubiquitous systems?
+\item user centered design?
+\item usability engineering?
+\item ...
+\end{itemize}
+\item Which of the found techniques can be reused?
+\item What can be improved?
+\end{itemize}
 

### 2012-11-30 paper/mswp2012-proposal.tex
finished first 2 phases of workpackages

@@
 
-Certainly we to not have to reinvent the wheel.
+Certainly we do not have to reinvent the wheel.
 Therefore a detailed literature research has to be carried out to find possible approaches that can be reused.
@@
 % --------------------------------------------------------------
+\newpage
 \section{Detailed description of the workpackages}
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 2-4 pages}
-\item Structuring the project into self-contained parts.
-\item Additional verbal descriptions.
-\item Work packages
-    \begin{itemize}
-    \item title
-    \item goal(s)
-    \item description
-    \item expected results
-    \item responsible person(s)
-    \item dependencies
-    \end{itemize}
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 2-4 pages}
+%\item Structuring the project into self-contained parts.
+%\item Additional verbal descriptions.
+%\item Work packages
+%    \begin{itemize}
+%    \item title
+%    \item goal(s)
+%    \item description
+%    \item expected results
+%    \item responsible person(s)
+%    \item dependencies
+%    \end{itemize}
+%\end{itemize}
+%}
+
+\subsection{Phase: Range of Functions}
+\label{sect:workplan:rangeoffucntions}
+
+\subsubsection{Literature Research LR1}
+\label{sect:workplan:phase1:lr1}
+\textbf{Dependencies:} None\\
+\textbf{Description:} Find and describe existing Systems and emphasis their approach.
+Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
+\textbf{Responsible person(s):} Research Group\\
+\textbf{Goal(s) and expected Results:} Information about current systems, their feature set and user-interface\\
+
+\subsubsection{Empirical Study ES1}
+\label{sect:workplan:phase1:es1}
+\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
+\textbf{Description:} Create questionary for users, to get information about their thoughts about the systems discovered in \ref{sect:workplan:phase1:lr1}.
+They should evaluate these results and discover issues with their User-Interface and functionality and also mention their needs regarding these two aspects.\\
+The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
+\textbf{Responsible person(s):} Research Group, Alpha-User \\
+\textbf{Goal(s) and expected Results:} Knowledge about the user needs.\\
+
+\subsubsection{Empirical Study ES2}
+\label{sect:workplan:phase1:es2}
+\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
+\textbf{Description:} Meeting with possible service partners (restaruants, supermarkets, doctors, etc.) to identify their currently used systems and their needs, thoughts and whishes and specify how a cooperation could look like.\\
+\textbf{Responsible person(s):} Strategy Team\\
+\textbf{Goal(s) and expected Results:} Knowledge about the needs of service partners. Signed partner contracts. \\
+
+\subsubsection{Range of Functions RF1}
+\label{sect:workplan:phase1:rf1}
+\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
+\textbf{Description:} Brainstorming about possible features of the system using knowledge discovered during step LR1 (\ref{sect:workplan:phase1:lr1}).\\
+\textbf{Responsible person(s):} Research Team\\
+\textbf{Goal(s) and expected Results:} Possible feature list\\
+
+\pagebreak
+\subsubsection{Range of Functions RF2}
+\label{sect:workplan:phase1:rf2}
+\textbf{Dependencies:} RF1 \ref{sect:workplan:phase1:rf1}, ES1 \ref{sect:workplan:phase1:es1}, ES2 \ref{sect:workplan:phase1:es2}\\
+\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the brainstormed feature list.
+Check if the discovered features from the empirical studies are matching the created feature list\\
+\textbf{Responsible person(s):} Research Team\\
+\textbf{Goal(s) and expected Results:} Final set of features for version 1.0 (Milestone M1)\\
+
+\subsection{Phase: Towards Release}
+\label{sect:workplan:towardsrelease}
+
+\subsubsection{Prototyping P1}
+\label{sect:workplan:phase2:p1}
+\textbf{Dependencies:} RF2 \ref{sect:workplan:phase1:rf2}\\
+\textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered.\\
+\textbf{Responsible person(s):} Dev-Team\\
+\textbf{Goal(s) and expected Results:} first version of prototype\\
+
+\subsubsection{Evaluation and Redesign ER1}
+\label{sect:workplan:phase2:er1}
+\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
+\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and redesign it by taking care of their input.
+This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
+\textbf{Responsible person(s):} Research-Group, Alpha-Users, Dev-Team\\
+\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype\\
+
+\subsubsection{Prototyping P2}
+\label{sect:workplan:phase2:p2}
+\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
+\textbf{Description:} Extend the existing prototype by adding functionality and implement the features.\\
+\textbf{Responsible person(s):} Dev-Team\\
+\textbf{Goal(s) and expected Results:} Prototype with all features\\
+
+\pagebreak
+\subsubsection{Evaluierung und Redesign ER2}
+\label{sect:workplan:phase2:er2}
+\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er2}\\
+\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev-Team (including Security and Quality Specialists).
+This step covers not only the interface and interaction, but also the quality and security of the product.
+The knowledge should be used to redesign the prototype and this step should be repeated several times.
+After a number of iterations the status of the web application should be switched to Beta and Beta-Users will be able to sign in and use the systems.
+After the last iteration the status should be switched to Release.\\
+\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev-Team\\
+\textbf{Goal(s) and expected Results:} Released web application (Milestone M2)\\
+
+\subsection{Phase: Connect to 3rd Party Services and mobile Client}
+\label{sect:workplan:3rdpartiesandmobileclient}
+
+\subsubsection{Literature Research LR2}
+\label{sect:workplan:phase3:lr2}
+\textbf{Goal(s):} \\
+\textbf{Dependencies:} \\
+\textbf{Description:} \\
+\textbf{Responsible person(s):} \\
+\textbf{Expected Results:} \\
+
+\subsubsection{Empirical Studie ES3}
+\label{sect:workplan:phase3:es2}
+\textbf{Goal(s):} \\
+\textbf{Dependencies:} \\
+\textbf{Description:} \\
+\textbf{Responsible person(s):} \\
+\textbf{Expected Results:} \\
+
+\subsubsection{Range of Function RF2}
+\label{sect:workplan:phase3:rf2}
+\textbf{Goal(s):} \\
+\textbf{Dependencies:} \\
+\textbf{Description:} \\
+\textbf{Responsible person(s):} \\
+\textbf{Expected Results:} \\
+
+\subsubsection{Range of Function RF3}
+\label{sect:workplan:phase3:rf3}
+\textbf{Goal(s):} \\
+\textbf{Dependencies:} \\
+\textbf{Description:} \\
+\textbf{Responsible person(s):} \\
+\textbf{Expected Results:} \\
+
+\subsubsection{Prototyping P3}
+\label{sect:workplan:phase3:p3}
+\textbf{Goal(s):} \\
+\textbf{Dependencies:} \\
+\textbf{Description:} \\
+\textbf{Responsible person(s):} \\
+\textbf{Expected Results:} \\
+
+\subsubsection{Evaluierung und Redesign ER3}
+\label{sect:workplan:phase3:er3}
+\textbf{Goal(s):} \\
+\textbf{Dependencies:} \\
+\textbf{Description:} \\
+\textbf{Responsible person(s):} \\
+\textbf{Expected Results:} \\
 
 % --------------------------------------------------------------
+\pagebreak
 \section{Time plan (Gantt chart)}

### 2012-11-30 paper/mswp2012-proposal.tex
finished workpackages

@@
 \textbf{Responsible person(s):} Research-Group, Alpha-Users, Dev-Team\\
-\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype\\
+\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\
 
@@
 \textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev-Team\\
-\textbf{Goal(s) and expected Results:} Released web application (Milestone M2)\\
+\textbf{Goal(s) and expected Results:} Released web application (Milestone M3)\\
 
@@
 \label{sect:workplan:phase3:lr2}
-\textbf{Goal(s):} \\
-\textbf{Dependencies:} \\
-\textbf{Description:} \\
-\textbf{Responsible person(s):} \\
-\textbf{Expected Results:} \\
+\textbf{Dependencies:} None\\
+\textbf{Description:} Collect Knowledge about ubiquitous systems and figure out, how the product can be transformed into such a system by providing apps for smartphones.
+Search for techniques using NFC, GPS, WiFi, etc.\\
+\textbf{Responsible person(s):} Research Team\\
+\textbf{Goal(s) and expected Results:} Knowledge about ubiquitous systems and mobile apps\\
 
 \subsubsection{Empirical Studie ES3}
-\label{sect:workplan:phase3:es2}
-\textbf{Goal(s):} \\
-\textbf{Dependencies:} \\
-\textbf{Description:} \\
-\textbf{Responsible person(s):} \\
-\textbf{Expected Results:} \\
+\label{sect:workplan:phase3:es3}
+\textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
+\textbf{Description:} Establish user needs regarding an mobile app and get infos about expectations of such an app \\
+\textbf{Responsible person(s):} Research Team, Users\\
+\textbf{Goal(s) and expected Results:} User needs regarding an mobile app\\
 
@@
 \label{sect:workplan:phase3:rf2}
-\textbf{Goal(s):} \\
-\textbf{Dependencies:} \\
-\textbf{Description:} \\
-\textbf{Responsible person(s):} \\
-\textbf{Expected Results:} \\
+\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
+\textbf{Description:} Convert the knowledge from ES3 to a feature list and requirements for an mobile application.\\
+\textbf{Responsible person(s):} Research Team\\
+\textbf{Goal(s) and expected Results:} Feature list, requirements and interaction concept for an mobile app\\
+
+\subsubsection{Prototyping P3}
+\label{sect:workplan:phase3:p3}
+\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
+\textbf{Description:} Implement mobile version of the system with prototyping\\
+\textbf{Responsible person(s):} Dev-Team\\
+\textbf{Goal(s) and expected Results:} Mobile clients\\
+
+\subsubsection{Empirical Studie ES4}
+\label{sect:workplan:phase3:es4}
+\textbf{Dependencies:} None\\
+\textbf{Description:} Establish if and which social health communities (e.g. tracking plattforms) our users are using and find out how to integrate these partner into the system. \\
+\textbf{Responsible person(s):} Research Team, Users\\
+\textbf{Goal(s) and expected Results:} Possible new partners (3rd party services)\\
 
@@
 \label{sect:workplan:phase3:rf3}
-\textbf{Goal(s):} \\
-\textbf{Dependencies:} \\
-\textbf{Description:} \\
-\textbf{Responsible person(s):} \\
-\textbf{Expected Results:} \\
-
-\subsubsection{Prototyping P3}
-\label{sect:workplan:phase3:p3}
-\textbf{Goal(s):} \\
-\textbf{Dependencies:} \\
-\textbf{Description:} \\
-\textbf{Responsible person(s):} \\
-\textbf{Expected Results:} \\
+\textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
+\textbf{Description:} Use information gained from ES4 to specify 3rd party services to integrate into the system e.g. by finding APIs etc.\\
+\textbf{Responsible person(s):} Research Team, Dev Team\\
+\textbf{Goal(s) and expected Results:} Features (services to integrate)\\
+
+\subsubsection{Prototyping P4}
+\label{sect:workplan:phase3:p4}
+\textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
+\textbf{Description:} Integrate established services into the system\\
+\textbf{Responsible person(s):} Dev Team\\
+\textbf{Goal(s) and expected Results:} System with integrated services\\
 
@@
 \label{sect:workplan:phase3:er3}
-\textbf{Goal(s):} \\
-\textbf{Dependencies:} \\
-\textbf{Description:} \\
-\textbf{Responsible person(s):} \\
-\textbf{Expected Results:} \\
+\textbf{Dependencies:} P3 \ref{sect:workplan:phase3:p3}, P4 \ref{sect:workplan:phase3:p4}\\
+\textbf{Description:} Evaluate and redesign the system and mobile clients by the users with several iterations.\\
+\textbf{Responsible person(s):} Dev Team, Users\\
+\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 2.0, Milestone M4)\\
 

### 2012-11-30 paper/mswp2012-proposal.tex
fixed some spelling mistakes

@@
 
-Analyzing these current systems you can find two strategies, on one hand the gamification of healthcare (see \ref{sect:star:gamification}) and on the other hand a combination of helathcare and social engineering with special plattforms.
+Analyzing these current systems you can find two strategies, on one hand the gamification of healthcare (see \ref{sect:star:gamification}) and on the other hand a combination of helathcare and social engineering with special platforms.
 
@@
 
-\paragraph{Social aspects:} The next step was to add social features to their plattforms to make this service more intersting for their users.
+\paragraph{Social aspects:} The next step was to add social features to their platforms to make this service more intersting for their users.
 They introduced a route-sharing feature, which makes it possible to find interesting routes near you posted by other runners.
@@
 
-\subsubsection{Similar Plattforms}
+\subsubsection{Similar Platforms}
 \label{sect:star:competitors}
-There are several other plattforms tracking your sport activities, a lot of them do not offer that many features as RunKeeper does, do not have that many users, or do not follow such an intense social approach.
+There are several other platforms tracking your sport activities, a lot of them do not offer that many features as RunKeeper does, do not have that many users, or do not follow such an intense social approach.
 
@@
 
-	One big advantage is the use of Xboxs Kinect which not only combine these two plattforms but also combine the two strategies of gamification and socialisation. \\
-	\item \textbf{Other plattforms introduced by several sport equipment manufactors:} Other manufactors like Polar also introduced their own plattforms but have problems to reach a big user-base.
-They tried to jump on this movement made by plattforms like RunKeeper or Runtastic, but couldn't get that much success with their systems, although they have a lot of success with their equipment.
+	One big advantage is the use of Xboxs Kinect which not only combine these two platforms but also combine the two strategies of gamification and socialisation. \\
+	\item \textbf{Other platforms introduced by several sport equipment manufactors:} Other manufactors like Polar also introduced their own platforms but have problems to reach a big user-base.
+They tried to jump on this movement made by platforms like RunKeeper or Runtastic, but couldn't get that much success with their systems, although they have a lot of success with their equipment.
 \end{itemize}
@@
 \textbf{Dependencies:} None\\
-\textbf{Description:} Find and describe existing Systems and emphasis their approach.
+\textbf{Description:} Find and describe existing systems and emphasis their approach.
 Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
@@
 \textbf{Description:} Create questionary for users, to get information about their thoughts about the systems discovered in \ref{sect:workplan:phase1:lr1}.
-They should evaluate these results and discover issues with their User-Interface and functionality and also mention their needs regarding these two aspects.\\
+They should evaluate these results and discover issues with their user-interface and functionality and also mention their needs regarding these two aspects.\\
 The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
@@
 \textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered.\\
-\textbf{Responsible person(s):} Dev-Team\\
+\textbf{Responsible person(s):} Dev Team\\
 \textbf{Goal(s) and expected Results:} first version of prototype\\
@@
 This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
-\textbf{Responsible person(s):} Research-Group, Alpha-Users, Dev-Team\\
+\textbf{Responsible person(s):} Research Group, Alpha-Users, Dev Team\\
 \textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\
@@
 \textbf{Description:} Extend the existing prototype by adding functionality and implement the features.\\
-\textbf{Responsible person(s):} Dev-Team\\
+\textbf{Responsible person(s):} Dev Team\\
 \textbf{Goal(s) and expected Results:} Prototype with all features\\
@@
 \textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er2}\\
-\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev-Team (including Security and Quality Specialists).
+\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev Team (including Security and Quality Specialists).
 This step covers not only the interface and interaction, but also the quality and security of the product.
@@
 After the last iteration the status should be switched to Release.\\
-\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev-Team\\
+\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev Team\\
 \textbf{Goal(s) and expected Results:} Released web application (Milestone M3)\\
@@
 \textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
-\textbf{Description:} Establish user needs regarding an mobile app and get infos about expectations of such an app \\
+\textbf{Description:} Establish user needs regarding an mobile app and get information about expectations of such an app \\
 \textbf{Responsible person(s):} Research Team, Users\\
@@
 \textbf{Description:} Implement mobile version of the system with prototyping\\
-\textbf{Responsible person(s):} Dev-Team\\
+\textbf{Responsible person(s):} Dev Team\\
 \textbf{Goal(s) and expected Results:} Mobile clients\\
@@
 \textbf{Dependencies:} None\\
-\textbf{Description:} Establish if and which social health communities (e.g. tracking plattforms) our users are using and find out how to integrate these partner into the system. \\
+\textbf{Description:} Establish if and which social health communities (e.g. tracking platforms) our users are using and find out how to integrate these partner into the system. \\
 \textbf{Responsible person(s):} Research Team, Users\\

### 2012-12-04 paper/mswp2012-proposal.tex
gantt

@@
 \textbf{Responsible person(s):} Research Team\\
-\textbf{Goal(s) and expected Results:} Final set of features for version 1.0 (Milestone M1)\\
+\textbf{Goal(s) and expected Results:} Final set of features for version 0.1 (Milestone M1)\\
 
@@
 \textbf{Responsible person(s):} Dev Team, Users\\
-\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 2.0, Milestone M4)\\
+\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 1.0, Milestone M4)\\
 

### 2012-12-05 paper/mswp2012-proposal.tex
Add method Thinking Aloud

@@
 
-\subsection{User Centered Design}
-\label{subsect:ucd}
-We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System.
-We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system.
-User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process.
-By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work.
-User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system.
-\\
-
-User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:
-
-\begin{enumerate}
-	\item Research Phase
-	\item Design Phase
-	\item Prototyping Phase
-	\item Evaluation Phase
-\end{enumerate}
-
-\begin{figure}[htb]
-	\centering
-		\includegraphics[width=0.8\textwidth]{images/method/UCD.pdf}
-	\caption{User Centered Design Process TODO MATTHIAS QUELLE ANGEBEN!}
-	\label{fig:UCD}
-\end{figure}
-
-During the \emph{Research Phase} information about the users, their profiles and their needs is collected.
-During the \emph{Design Phase} the requirements are specified based on the information gathered in the research phase and the concepts are created.
-During the \emph{Prototyping Phase} various forms of mockups and prototypes are created based on the information gathered in the design phase.
-In the \emph{Evaluation Phase} the prototypes and mockups are finally discussed with the users and evaluated.
-It is important to repeatedly check if the needs of the users are still met.
-Therefore the phases are interconnected and fast iteration is a vital part of User Centered Design.
-
-\subsection{Experimental Horizontal Prototyping}
-We decided for a combination of experimental and horizontal prototyping as software development method.
-
-Experimental prototyping aims at creating a prototype of the system in an early phase of the development process and is therefore highly compatible with the use of user centered design (see \ref{subsect:ucd}).
-There is also a connection to the empirical study part (see \ref{subsect:emp_study}), as the prototype shall be used for evaluating requirements of users as well as of partners from the industry.
-Not only should an early prototype lead to a higher-sophisticated user interface with respect to ui design principles and usability issues, but also provide possibility to gain results for the research part of the overall project.
-
-The prototyping shall be executed in a horizontal manner, that means there should be a fully designed user interface before starting over with any kind of business logic implementation.
-In contrast to that, vertical prototyping aims at implementing one specific feature from the frontend to the backend with its full functionality.
-The advantage of an horizontal approach is, similar to an experimental one, the perfect compatibility with user centered design.
-Of course this requires a strict separation of user interface and business logic implementation.
-See figure \ref{fig:prototyping} for a distinction between horizontal and vertical prototyping.
-
-\begin{figure}[htb]
-	\centering
-		\includegraphics[width=0.6\textwidth]{images/method/prototyping}
-	\caption{Horizontal and vertical prototyping \citep[Page 94]{DBLP:books/daglib/0076830}}
-	\label{fig:prototyping}
-\end{figure}
-
-One advantage of prototyping is that potential errors in the user interface can be detected in an early phase of the project - also quality assurance can get embedded into the project as early as possible.
-
-\subsection{Empirical Study}
-\label{subsect:emp_study}
-
-Empirical study of the needs of the main stakeholders in the project is essential.
-By means of surveys and interviews we try to identify requirements and hope to get answers to the following (and more) questions:
-
-\begin{itemize}
-\item What do end users need/want? What is negligible and can therefore be omitted?
-\item What do they miss in actual systems?
-\item How do they wish to interact with the system?
-\item What are the needs of the different business partners?
-\item Which systems are currently in use at the partners processes?
-\item How would they improve their current systems?
-\end{itemize}
-
-Of course empirical study has to take place at a very early phase in the project to prevent undesirable development and ensure movement into the right direction from the very beginning.
-The contents of the questionnaire therefore have to be prepared conscientiously and meaningful, so that as much findings as possible can be deduced for use in later phases of the project.
-
-\subsection{Literature Research}
-
-Certainly we do not have to reinvent the wheel.
-Therefore a detailed literature research has to be carried out to find possible approaches that can be reused.
-By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others projects.
-The literature research part aims at answering the following questions
-
-\begin{itemize}
-\item Which techniques are already in use or have been introduced in the field of
-\begin{itemize}
-\item healthcare applications?
-\item ubiquitous systems?
-\item user centered design?
-\item usability engineering?
-\item ...
-\end{itemize}
-\item Which of the found techniques can be reused?
-\item What can be improved?
-\end{itemize}
-
 %\note{
@@
 %}
+
+\subsection{User Centered Design}
+\label{subsect:ucd}
+We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System.
+We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system.
+User Centered Design is an iterative process that aims at supporting this procedure by integrating the user early into the design process.
+By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work.
+User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system.
+\\
+
+User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:
+
+\begin{enumerate}
+	\item Research Phase
+	\item Design Phase
+	\item Prototyping Phase
+	\item Evaluation Phase
+\end{enumerate}
+
+\begin{figure}[htb]
+	\centering
+		\includegraphics[width=0.8\textwidth]{images/method/UCD.pdf}
+	\caption{User Centered Design Process TODO MATTHIAS QUELLE ANGEBEN!}
+	\label{fig:UCD}
+\end{figure}
+
+During the \emph{Research Phase} information about the users, their profiles and their needs is collected.
+During the \emph{Design Phase} the requirements are specified based on the information gathered in the research phase and the concepts are created.
+During the \emph{Prototyping Phase} various forms of mockups and prototypes are created based on the information gathered in the design phase.
+In the \emph{Evaluation Phase} the prototypes and mockups are finally discussed with the users and evaluated.
+It is important to repeatedly check if the needs of the users are still met.
+Therefore the phases are interconnected and fast iteration is a vital part of User Centered Design.
+
+\subsection{Experimental Horizontal Prototyping}
+We decided for a combination of experimental and horizontal prototyping as software development method.
+
+Experimental prototyping aims at creating a prototype of the system in an early phase of the development process and is therefore highly compatible with the use of user centered design (see \ref{subsect:ucd}).
+There is also a connection to the empirical study part (see \ref{subsect:emp_study}), as the prototype shall be used for evaluating requirements of users as well as of partners from the industry.
+Not only should an early prototype lead to a higher-sophisticated user interface with respect to ui design principles and usability issues, but also provide possibility to gain results for the research part of the overall project.
+
+The prototyping shall be executed in a horizontal manner, that means there should be a fully designed user interface before starting over with any kind of business logic implementation.
+In contrast to that, vertical prototyping aims at implementing one specific feature from the frontend to the backend with its full functionality.
+The advantage of an horizontal approach is, similar to an experimental one, the perfect compatibility with user centered design.
+Of course this requires a strict separation of user interface and business logic implementation.
+See figure \ref{fig:prototyping} for a distinction between horizontal and vertical prototyping.
+
+\begin{figure}[htb]
+	\centering
+		\includegraphics[width=0.6\textwidth]{images/method/prototyping}
+	\caption{Horizontal and vertical prototyping \citep[Page 94]{DBLP:books/daglib/0076830}}
+	\label{fig:prototyping}
+\end{figure}
+
+One advantage of prototyping is that potential errors in the user interface can be detected in an early phase of the project - also quality assurance can get embedded into the project as early as possible.
+
+\subsection{Thinking Aloud}
+\label{subsect:think_aloud}
+
+Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Nielsen.
+It involves participants thinking aloud as they perform certain tasks.
+The participants are asked to say whatever they are thinking about, looking at, doing or feeling while performing the tasks.
+Observers take notes of everything the participant says during the scenario without attempting to interpret their claims.
+The sessions are usually recorded to enable you to go back later and connect the claims with the tasks the participant was currently performing.
+The purpose of this method is to make assumptions explicit.
+By explicitely saying their thoughts, it gets easier to understand how the participants view the system and to identify their major misconceptions.
+It helps reveiling \emph{why} users do something.
+It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems.
+
+\subsection{Empirical Study}
+\label{subsect:emp_study}
+
+Empirical study of the needs of the main stakeholders in the project is essential.
+By means of surveys and interviews we try to identify requirements and hope to get answers to the following (and more) questions:
+
+\begin{itemize}
+\item What do end users need/want? What is negligible and can therefore be omitted?
+\item What do they miss in actual systems?
+\item How do they wish to interact with the system?
+\item What are the needs of the different business partners?
+\item Which systems are currently in use at the partners processes?
+\item How would they improve their current systems?
+\end{itemize}
+
+Of course empirical study has to take place at a very early phase in the project to prevent undesirable development and ensure movement into the right direction from the very beginning.
+The contents of the questionnaire therefore have to be prepared conscientiously and meaningful, so that as much findings as possible can be deduced for use in later phases of the project.
+
+\subsection{Literature Research}
+
+Certainly we do not have to reinvent the wheel.
+Therefore a detailed literature research has to be carried out to find possible approaches that can be reused.
+By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others projects.
+The literature research part aims at answering the following questions
+
+\begin{itemize}
+\item Which techniques are already in use or have been introduced in the field of
+\begin{itemize}
+\item healthcare applications?
+\item ubiquitous systems?
+\item user centered design?
+\item usability engineering?
+\item ...
+\end{itemize}
+\item Which of the found techniques can be reused?
+\item What can be improved?
+\end{itemize}
 

### 2012-12-05 paper/mswp2012-proposal.tex
Add reference to Nielsen

@@
 		\includegraphics[width=0.6\textwidth]{images/method/prototyping}
-	\caption{Horizontal and vertical prototyping \citep[Page 94]{DBLP:books/daglib/0076830}}
+	\caption{Horizontal and vertical prototyping \citep[Page 94]{nielsen1994}}
 	\label{fig:prototyping}
@@
 
-Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Nielsen.
+Thinking Aloud is a method developed in the usability testing labs of IBM and is one of the most valuable usability engineering methods according to Jakob Nielsen \citep[Page 195ff]{nielsen1994}.
 It involves participants thinking aloud as they perform certain tasks.
@@
 \item usability engineering?
-\item ...
 \end{itemize}

### 2012-12-05 paper/mswp2012-proposal.tex
Trying to add some more justifications for used methods

@@
 \label{subsect:ucd}
-We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System.
+We decided on \emph{User Centered Design} as the procedure model used to accompany the creation of the Modern Health Care System because it is a structured method that involves the end users throughout all stages of the design and development of our system.
 We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system.
@@
 \subsection{Experimental Horizontal Prototyping}
-We decided for a combination of experimental and horizontal prototyping as software development method.
+We decided for a combination of experimental and horizontal prototyping as software development method because it perfectly fits into the overall procedure model.
+By creating an horizontal prototype in an early state and iterating it with the information gathered from our users we aim at creating a highly usable product with reasonable costs.
 
@@
 By explicitely saying their thoughts, it gets easier to understand how the participants view the system and to identify their major misconceptions.
-It helps reveiling \emph{why} users do something.
-It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems.
+\\
+
+We choose to use Thinking Aloud during the conception of the Modern Health Care System because it helps reveiling \emph{why} users do something.
+It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems and this ultimately leads to a better system and reduced costs.
 
@@
 Empirical study of the needs of the main stakeholders in the project is essential.
-By means of surveys and interviews we try to identify requirements and hope to get answers to the following (and more) questions:
+Creating a product that does either not suit the workflow of the desired users or doesn't gain any traction for viable business partners would be a failure of the project.
+By means of surveys and interviews we try to identify requirements at the beginning and aim at getting answers to at least the following questions:
 
@@
 \item What do end users need/want? What is negligible and can therefore be omitted?
-\item What do they miss in actual systems?
+\item What do they miss in current systems?
 \item How do they wish to interact with the system?
@@
 
-Certainly we do not have to reinvent the wheel.
-Therefore a detailed literature research has to be carried out to find possible approaches that can be reused.
-By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others projects.
-The literature research part aims at answering the following questions
+Certainly we do not have to and do not intent to reinvent the wheel with the Modern Health Care System, therefore a detailed literature research has to be carried out to find possible approaches that are already tested and can be reused.
+By finding other scientific work at the same topics we want to save both time and unnecessary work that has already been done by others and concentrate on the questions that haven't been answered yet.
+\\
+
+The literature research part aims at answering the following questions:
 
@@
 \item What can be improved?
+\item Which research questions are still open to answer?
 \end{itemize}

### 2012-12-05 paper/mswp2012-proposal.tex
Minimally add some more infos answering the question 'how should the expected results be achieved?'

@@
 By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work.
-User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system.
-\\
+This enables us to get a better understanding of the actual needs of the users and how to solve their problems by the means of an effective and fun to use system.
+Moreover we get a better understanding of the motivation and psychological profile of our users, which should help gathering knowledge in the field of gamification.
+
+User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods that more often emphasize on functionality and robustness of the system. \\
 
@@
 We choose to use Thinking Aloud during the conception of the Modern Health Care System because it helps reveiling \emph{why} users do something.
+It helps us focusing on the interaction needs of the users and to develop a highly integrated ubiquitous system.
 It is very important to integrate Thinking Aloud in a very early stage of the design and development process because early clues can help anticipating and tracing the source of problems and this ultimately leads to a better system and reduced costs.

### 2012-12-06 paper/mswp2012-proposal.tex
extended WBS a little bit and removed unnecessary (s)

@@
 		\includegraphics[width=0.8\textwidth]{images/method/UCD.pdf}
-	\caption{User Centered Design Process TODO MATTHIAS QUELLE ANGEBEN!}
+	\caption{User Centered Design Process [\cite{usability11}]}
 	\label{fig:UCD}
@@
 %    \item title
-%    \item goal(s)
+%    \item Goals
 %    \item description
 %    \item expected results
-%    \item responsible person(s)
+%    \item responsible persons
 %    \item dependencies
@@
 Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
-\textbf{Responsible person(s):} Research Group\\
-\textbf{Goal(s) and expected Results:} Information about current systems, their feature set and user-interface\\
+\textbf{Responsible persons:} Research Group\\
+\textbf{Goals and expected Results:} Information about current systems, their feature set and user-interface\\
 
@@
 The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
-\textbf{Responsible person(s):} Research Group, Alpha-User \\
-\textbf{Goal(s) and expected Results:} Knowledge about the user needs.\\
+\textbf{Responsible persons:} Research Group, Alpha-User \\
+\textbf{Goals and expected Results:} Knowledge about the user needs.\\
 
@@
 \textbf{Description:} Meeting with possible service partners (restaruants, supermarkets, doctors, etc.) to identify their currently used systems and their needs, thoughts and whishes and specify how a cooperation could look like.\\
-\textbf{Responsible person(s):} Strategy Team\\
-\textbf{Goal(s) and expected Results:} Knowledge about the needs of service partners. Signed partner contracts. \\
+\textbf{Responsible persons:} Strategy Team\\
+\textbf{Goals and expected Results:} Knowledge about the needs of service partners. Signed partner contracts. \\
 
@@
 \textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
-\textbf{Description:} Brainstorming about possible features of the system using knowledge discovered during step LR1 (\ref{sect:workplan:phase1:lr1}).\\
-\textbf{Responsible person(s):} Research Team\\
-\textbf{Goal(s) and expected Results:} Possible feature list\\
+\textbf{Description:} Evaluating and complete feature set using knowledge discovered during step LR1 (\ref{sect:workplan:phase1:lr1}).\\
+\textbf{Responsible persons:} Research Team\\
+\textbf{Goals and expected Results:} Next draft of  feature list\\
 
@@
 \textbf{Dependencies:} RF1 \ref{sect:workplan:phase1:rf1}, ES1 \ref{sect:workplan:phase1:es1}, ES2 \ref{sect:workplan:phase1:es2}\\
-\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the brainstormed feature list.
-Check if the discovered features from the empirical studies are matching the created feature list\\
-\textbf{Responsible person(s):} Research Team\\
-\textbf{Goal(s) and expected Results:} Final set of features for version 0.1 (Milestone M1)\\
+\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the provisory feature list.
+Check if the discovered features from the empirical studies are matching the created feature list.
+Which features are really necessary and have an actual benefit for the users and stackholders?
+Which features are just nice to have or unnecessary at all?\\
+\textbf{Responsible persons:} Research Team\\
+\textbf{Goals and expected Results:} Final set of features for version 0.1 (Milestone M1)\\
 
@@
 \textbf{Dependencies:} RF2 \ref{sect:workplan:phase1:rf2}\\
-\textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered.\\
-\textbf{Responsible person(s):} Dev Team\\
-\textbf{Goal(s) and expected Results:} first version of prototype\\
+\textbf{Description:} Create first version of horizontal prototype by creating the user-interface.
+Every part of the system should be covered to make an evaluation of this prototype by a group of Alpha-Users possible.
+The users should get an idea how to use the product and experience the interaction.\\
+\textbf{Responsible persons:} Dev Team\\
+\textbf{Goals and expected Results:} first version of prototype\\
 
@@
 \textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
-\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and redesign it by taking care of their input.
+\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and the Dev-Team should redesign it by taking care of their input.
 This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
-\textbf{Responsible person(s):} Research Group, Alpha-Users, Dev Team\\
-\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\
+\textbf{Responsible persons:} Research Group, Alpha-Users, Dev Team\\
+\textbf{Goals and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\
 
@@
 \textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
-\textbf{Description:} Extend the existing prototype by adding functionality and implement the features.\\
-\textbf{Responsible person(s):} Dev Team\\
-\textbf{Goal(s) and expected Results:} Prototype with all features\\
+\textbf{Description:} Extend the existing prototype by adding functionality and implement the features. The prototype should extend the first version to create and get real data and not only stubs.\\
+\textbf{Responsible persons:} Dev Team\\
+\textbf{Goals and expected Results:} Prototype with all features as a base for the next evaluation step and the first release.\\
 
@@
 \label{sect:workplan:phase2:er2}
-\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er2}\\
+\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er1}\\
 \textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev Team (including Security and Quality Specialists).
@@
 After the last iteration the status should be switched to Release.\\
-\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev Team\\
-\textbf{Goal(s) and expected Results:} Released web application (Milestone M3)\\
+\textbf{Responsible persons:} Alpha-Users, Beta-Users, Strategy Team, Dev Team\\
+\textbf{Goals and expected Results:} Released web application (Milestone M3)\\
 
@@
 \textbf{Description:} Collect Knowledge about ubiquitous systems and figure out, how the product can be transformed into such a system by providing apps for smartphones.
-Search for techniques using NFC, GPS, WiFi, etc.\\
-\textbf{Responsible person(s):} Research Team\\
-\textbf{Goal(s) and expected Results:} Knowledge about ubiquitous systems and mobile apps\\
+Search for techniques using NFC, GPS, WiFi, etc.
+Investigate research topics using these techniques like localization, payment, and so on.\\
+\textbf{Responsible persons:} Research Team\\
+\textbf{Goals and expected Results:} Knowledge about ubiquitous systems and mobile apps\\
 
@@
 \textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
-\textbf{Description:} Establish user needs regarding an mobile app and get information about expectations of such an app \\
-\textbf{Responsible person(s):} Research Team, Users\\
-\textbf{Goal(s) and expected Results:} User needs regarding an mobile app\\
+\textbf{Description:} Establish user needs regarding an mobile app and get information about expectations of such an app.
+Find out how the user would use such an app and how this app would influence his daily life.
+Find ways to embedd this application in the users daily workflow and figure out, how the users could gain more benefits out of the product by providing such an mobile application.\\
+\textbf{Responsible persons:} Research Team, Users\\
+\textbf{Goals and expected Results:} User needs regarding an mobile app\\
 
@@
 \textbf{Description:} Convert the knowledge from ES3 to a feature list and requirements for an mobile application.\\
-\textbf{Responsible person(s):} Research Team\\
-\textbf{Goal(s) and expected Results:} Feature list, requirements and interaction concept for an mobile app\\
-
+\textbf{Responsible persons:} Research Team\\
+\textbf{Goals and expected Results:} Feature list, requirements and interaction concept for an mobile app\\
+
+\pagebreak
 \subsubsection{Prototyping P3}
@@
 \textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
-\textbf{Description:} Implement mobile version of the system with prototyping\\
-\textbf{Responsible person(s):} Dev Team\\
-\textbf{Goal(s) and expected Results:} Mobile clients\\
+\textbf{Description:} Implement mobile version of the system with prototyping.
+Features should include localization of the user to know, if the user is accessing establishment of service partner (e.g.
+restaurant, fitness center, etc.) and simple tracking of the users activities through NFC, QR-Code-Reader, etc.\\
+\textbf{Responsible persons:} Dev Team\\
+\textbf{Goals and expected Results:} Mobile clients\\
 
@@
 \textbf{Description:} Establish if and which social health communities (e.g. tracking platforms) our users are using and find out how to integrate these partner into the system. \\
-\textbf{Responsible person(s):} Research Team, Users\\
-\textbf{Goal(s) and expected Results:} Possible new partners (3rd party services)\\
+\textbf{Responsible persons:} Research Team, Users\\
+\textbf{Goals and expected Results:} Possible new partners (3rd party services)\\
 
@@
 \textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
-\textbf{Description:} Use information gained from ES4 to specify 3rd party services to integrate into the system e.g. by finding APIs etc.\\
-\textbf{Responsible person(s):} Research Team, Dev Team\\
-\textbf{Goal(s) and expected Results:} Features (services to integrate)\\
+\textbf{Description:} Use information gained from ES4 to specify 3rd party services to integrate into the system e.g.
+by finding APIs etc.
+It should be possible to e.g.
+include your sport activities from sport communities by using their API.\\
+\textbf{Responsible persons:} Research Team, Dev Team\\
+\textbf{Goals and expected Results:} Features (services to integrate)\\
 
@@
 \textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
-\textbf{Description:} Integrate established services into the system\\
-\textbf{Responsible person(s):} Dev Team\\
-\textbf{Goal(s) and expected Results:} System with integrated services\\
+\textbf{Description:} Integrate established services into the system and create nice and intuitive interface to access these informations.\\
+\textbf{Responsible persons:} Dev Team\\
+\textbf{Goals and expected Results:} System with integrated services\\
 
@@
 \textbf{Description:} Evaluate and redesign the system and mobile clients by the users with several iterations.\\
-\textbf{Responsible person(s):} Dev Team, Users\\
-\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 1.0, Milestone M4)\\
+\textbf{Responsible persons:} Dev Team, Users\\
+\textbf{Goals and expected Results:} Redesigned system and mobile clients (Version 1.0, Milestone M4)\\
 

### 2012-12-06 paper/mswp2012-proposal.tex
gantt

@@
 \usepackage{color}
+\usepackage{subfigure}
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 1-2 pages}
-\item Realistic estimation of schedule based on workpackages.
-\item Including milestones (not only when but also what is to be achieved for each milestone).
-\item Generation of a Gantt chart. (Including phases, milestones, buffer times, critical areas, etc.)
-\end{itemize}
-}
+\begin{figure}\centering
+\subfigure[part 2]{\includegraphics[width=5cm]{images/gantt/Gantt_part12.png}}
+\subfigure[part 1]{\includegraphics[width=5cm]{images/gantt/Gantt_part1.png}}
+\caption{Gantt Chart}
+\end{figure}
+
+\begin{figure}\centering
+\subfigure[part 4]{\includegraphics[width=5cm]{images/gantt/Gantt_part22.png}}
+\subfigure[part 3]{\includegraphics[width=5cm]{images/gantt/Gantt_part2.png}}
+\caption{Gantt Chart}
+\end{figure}
+
+%\note{
+%\begin{itemize}
+%\item {\em Length: 1-2 pages}
+%\item Realistic estimation of schedule based on workpackages.
+%\item Including milestones (not only when but also what is to be achieved for each milestone).
+%\item Generation of a Gantt chart. (Including phases, milestones, buffer times, critical areas, etc.)
+%\end{itemize}
+%}
+
+%\begin{figure}[h]
+%\centering
+%\begin{minipage}{.4\textwidth}
+%\includegraphics[width=6cm]{images/gantt/Gantt_part1.png}
+%\caption{Gantt part 1}
+%\label{fig:ganttpart1}
+%\end{minipage}
+%\begin{minipage}{.4\textwidth}
+%\includegraphics[width=6cm]{images/gantt/Gantt_part2.png}
+%\caption{Gantt part 2}
+%\label{fig:ganttpart2}
+%\end{minipage}
+%\end{figure}
 

### 2012-12-27 paper/mswp2012-proposal.tex
pagebreak bei gantt
added chapter Human Resources/Team

@@
 % --------------------------------------------------------------
-\pagebreak
 \section{Time plan (Gantt chart)}
@@
 
+\pagebreak
+
 % --------------------------------------------------------------
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 1-2 pages}
-\item Description of the team that is needed to carry out the project. (For the execution phase of the project, not the planning phase.)
-\item How many people?
-\item To what extent are individual members needed?
-\item What knowledge, skills, and experiences are needed for each member?
-\item Demonstrate that the members will be able to carry out the project successfully.
-\item Work structure
-	\begin{itemize}
-	\item     Who will lead the project?
-	\item     How do they work together?
-	\item     Management and coordination
-		\begin{itemize}
-		\item 	        What communication structures will be established? (e.g., mailing list, blog, CMS, CVS, ...)
-		\item 	        How often will meetings take place? (Who will participate?)
-		\item 	        How will the work be documented?
-		\item 	        How will information be stored and shared?
-		\end{itemize}
-	\end{itemize}
-\item Cooperations
-	\begin{itemize}
-	\item     Will external cooperators be part of the project? (e.g., other research institutions or companies)
-	\item     What is their role?
-	 \item    Why are they needed?
-	\end{itemize}
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 1-2 pages}
+%\item Description of the team that is needed to carry out the project. (For the execution phase of the project, not the planning phase.)
+%\item How many people?
+%\item To what extent are individual members needed?
+%\item What knowledge, skills, and experiences are needed for each member?
+%\item Demonstrate that the members will be able to carry out the project successfully.
+%\item Work structure
+%	\begin{itemize}
+%	\item     Who will lead the project?
+%	\item     How do they work together?
+%	\item     Management and coordination
+%		\begin{itemize}
+%		\item 	        What communication structures will be established? (e.g., mailing list, blog, CMS, CVS, ...)
+%		\item 	        How often will meetings take place? (Who will participate?)
+%		\item 	        How will the work be documented?
+%		\item 	        How will information be stored and shared?
+%		\end{itemize}
+%	\end{itemize}
+%\item Cooperations
+%	\begin{itemize}
+%	\item     Will external cooperators be part of the project? (e.g., other research institutions or companies)
+%	\item     What is their role?
+%	 \item    Why are they needed?
+%	\end{itemize}
+%\end{itemize}
+%}
+
+\subsection{Teams}
+\subsubsection{Strategy Team}
+The Strategy Team is responsible for leading the project and handling the most importing decisions as well as keeping it all together and assuring the quality of the product. \\
+
+The \textbf{project manager} will be the head of the project and will be assisted by his co project manager during all phases and as a backup in case of unforseeable circuumstances.
+One of them should also have a funded technical knowledge, the other expirenced in economical topics.
+Both should work as a team and also handle the ressource management and trigger the planned phases.
+\\
+
+Another very importent rule to fill will be the \textbf{Quality manager}.
+This person will create the quality plan, organize reviews and check, if the corresponding plan is also executed like intended.
+\\
+
+Just before the release of Version 1.0 two people will join the team to undertake marketing tasks from the project managers.
+
+Therefore the number of members of the Strategy Team will increase from \textbf{three people} at the beginning to \textbf{five people} before the first release.
+
+\subsubsection{Research Team}
+This team will be responsible for research topics, therefore experience in scientific area is mandatory for them.
+They will also lead the user interviews with Alpha- and Beta-User and prepare these interviews by collecting knowledge through research of the state-of-the-art methods and systems.
+\\
+
+The results of the user interviews will be analyzed and statistically evaluated by this team to get the best advantage out of it and enhance the product.
+
+They are also responsible for market analysis and observation of customer needs. \\
+
+The team will include \textbf{three experts} at the start of the project and will \textbf{increase to five people} in the middle of the project.
+
+\subsubsection{Dev Team}
+There will be several Dev Teams with different main aspects to cover, but whatsoever there will be couple of poeple that will be responsible for small parts of each team.
+
+On of these experts will be the \textbf{Security Expert}.
+This person will be responsible for all the security issues regarding data storage, anonymization of personal information of the users, reliability, recovery, etc.
+He will also make choices regarding server selection and managing the infrastructure.
+At the end of the project another Security Expert will join as backup and support.
+\\
+
+Two \textbf{Usability and Design Engineers} will be part of the project from the beginning to develop design guidelines and also lead the project from the first prototype to the final product regarding interface and interaction design.
+
+These engineers should also have experience in designing mobile clients, because the design of the mobile application will also be part of their work. \\
+
+The team to start development will be the \textbf{Web Dev Team} and be responsible for the web client and the background services.
+Therefore knowledge of HTML5, CSS, JavaScript and additional programming languages to implement a backend is required.
+The size of the team will be between \textbf{six and ten people}, depending on the project progress.
+\\
+
+Additional a \textbf{Mobile Dev Team} will join to implment mobile clients for the project.
+Only iOS and Android clients are planned until version 2.0 therefore knowledge in iOS and/or Android programming is mandatory.
+The size of this team should be between \textbf{three and five people}.
+
+\subsection{Work structure}
+
+\subsubsection{Weekly Joure Fix}
+Every week there will be a meeting with all responsible persons including the project managers, quality managers, lead engineers (person from each dev-team, usability and design engineers, security engineer, etc.) and the lead of the research team to discuss the current progress of the project and the next steps.
+
+\subsubsection{Reviews}
+The Quality Manager will held several reviews to check the project documentation, the execution of test plans and results from the user-interviews.
+Therefore he will be in contact with the research team as well as with the dev team.
+
+\subsubsection{Scrum}
+As development process scrum should be used.
+There will be one person in each dev team which is the manager of its own small group to make communication easier with the project manager.
+This person will check during the daily scrum meeting the progress of this small group.
+Once a week the project manager will meet the team to check the overall progress, he is also responsible fro defining the product backlog for the next sprint.
+
+\subsubsection{Communication and Documentation}
+For each team there will be a seperate mailing list to distribute messages to the whole team.
+
+Additional there will be two blogs. The first one will be handling the internal communication inside the company, covering news for all employees, strategy decisions and so one. \\
+
+The official blog will be used as communication channel to the users and the community and will also be used to publish scientifical relevant results from the research group as well as results from user interviews.
+\\
+
+The created project documentation will be stored in the configuration management tool, which will also handle access control and versioning.
+This tool will be set up by the strategy team before the project start.
+
+\pagebreak
 

### 2012-12-29 paper/mswp2012-proposal.tex
Add security introduction

@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 1-2 pages}
-\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
-\item Are there any security-sensitive issues that apply to your proposal?
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 1-2 pages}
+%\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
+%\item Are there any security-sensitive issues that apply to your proposal?
+%\end{itemize}
+%}
+
+Whenever personal data is stored in a centralized system discussions about security and privacy arise - this is especially true for sensible data like illnesses.
+Since the modern health care system deals with very sensible and personal data, security and privacy are two very important issue to deal with and we need to take the seriously.
+
+By combining data from various sources the modern health care system is able to create a detailed health report of each and every participant and we need to make sure that these reports are anonymized and secured against attacks.
 

### 2012-12-29 paper/mswp2012-proposal.tex
Most ethical project ever

--- 2012-12-27 paper/mswp2012-proposal.tex
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 1-2 pages}
-\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
-\item Are there any security-sensitive issues that apply to your proposal?
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 1-2 pages}
+%\item Provide a brief explanation of the ethical issue involved and how it will be dealt with appropriately.
+%\item Are there any security-sensitive issues that apply to your proposal?
+%\end{itemize}
+%}
+
+Whenever personal data is stored in a centralized system discussions about security and privacy arise - this is especially true for sensible data like illnesses and health records.
+Since the modern health care system deals with very sensible and personal data, security and privacy are two very important issue to deal with and we need to take them seriously.
+\\
+
+By combining data from various different sources the modern health care system is able to create a detailed health report of each and every participant and we need to make sure that these reports are anonymized and secured against attacks from outside as well as inside.
+From an ethical point of view the modern health care system performs research on humans and the collected data threatens the participants' privacy.
+\\
+
+The modern health care system performs research on humans and involves patients and human data collection.
+Therefore ethical issues arise.
+Ethics aren't to be confused with behaving in accordance with social conventions, beliefs and laws - Tomas Paul and Linda Elder define ethics as \emph{a set of concepts and principles that guide us in determining what behavior helps or harms sentient creatures} [\cite{paul2006thinker}].
+\\
+
+The ethical issues that arise for the modern health care system are the following:
+
+\begin{itemize}
+	\item \textbf{Respect for autonomy}: the participant has the right to stop the participation whenever he wants to.
+All data associated with his record needs to be permanetly deleted and removed from our databases.
+	\item \textbf{Respect for persons}: the participant has the right to be treated with dignity.
+	\item \textbf{Right for inquiry}: the participant has the right to be informed about all the data associated with his record.
+	\item \textbf{Truthfulness and honesty}: the participant must not be misinformed about the information derived from his record and how this information was derived.
+	\item \textbf{Privacy} the participant has the right that all the information associated with his record is kept private and secured against unpurposeful usage.
+\end{itemize}
+
+We deal with these issues accordingly:
+
+\paragraph{Respect for autonomy}
+The modern health care system provides a way for each participant to exit our study and remove all his data from our records by the means of an online form.
+The participant can optionally attach information about the reasons why he is leaving the study.
+
+\paragraph{Respect for persons}
+Every participant of the modern health care system is treated in the same way, regardless of his health condition, culture, religion or any other data associated with his record.
+
+\paragraph{Right for inquiry}
+The modern health care system provides an online form similar to current social networks that enables the participants to receive a detailed record about all the data associated with their record.
+
+\paragraph{Truthfulness and honesty}
+The record containing the information about all the data associated with a participants record is created as detailed as possible.
+Furthermore, whenever the modern health care system derives a possible health risk from the participants condition and actions recorded an information is provided why the system considers the current situation a risk.
+
+\paragraph{Privacy}
+Data privacy is ensured by today's means.
+We use state-of-the-art security and privacy algorithms to keep our data as secure as possible.
+Of course, as always, security can't be fully guaranteed, but we highly respect our responsibility of keeping all the data as secure as possible.
+By picking the most suitable algoriths for data obsfuscation like Partitioning, Randomization or Group Based Anonymization we make it as hard as possible to associate given data with a specific participant.
+Furthermore all our data is stored encrypted and the communication over the internet is performed encrypted as well as over secure channels.
 

### 2013-01-05 paper/mswp2012-proposal.tex
11. implications and risks

@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 1-2 pages}
-\item Importance of the expected results for the discipline
-	\begin{itemize}
-	\item     To what extent does the proposed research address important challenges?
-	\end{itemize}
-\item Importance of the expected results for other areas
-\item What are possible risks of the project and how can they be alleviated?
-	\begin{itemize}
-	\item     What factors could lead to a failure of the project?
-	\item     Which factors or persons could support the project and increase the chance for success?
-	\item     What if important team members leave the project?
-	\end{itemize}
-\end{itemize}
-}
+%\note{
+%\begin{itemize}
+%\item {\em Length: 1-2 pages}
+%\item Importance of the expected results for the discipline
+%	\begin{itemize}
+%	\item     To what extent does the proposed research address important challenges?
+%	\end{itemize}
+%\item Importance of the expected results for other areas
+%\item What are possible risks of the project and how can they be alleviated?
+%	\begin{itemize}
+%	\item     What factors could lead to a failure of the project?
+%	\item     Which factors or persons could support the project and increase the chance for success?
+%	\item     What if important team members leave the project?
+%	\end{itemize}
+%\end{itemize}
+%}
+
+\subsection{Importance of the expected results}
+
+The main challenge to overcome with this project is to motivate people to live healthier.
+As we try to combine modern techniques with approved health care measures we hope to encourage the user to utilize the system as often as possible.
+This should lead to concrete health improvements of each individual user.
+The research part of the project shall lead to ground-breaking findings in the section of user interface design for ubiquitous technical health case assistants.
+As there is currently no comparable system, by means of dimension, the possible target group of users is very big.
+
+Not only individuals shall benefit from the results of our project, but whole communities.
+Healthier people lead to long-term savings in health care expenditures.
+States and health insurance funds will be able to save a lot of investments.
+
+\subsection{Possible risks}
+
+\subsubsection{Failure risks}
+One possible failure risk is the drop-out of team members during project runtime. This is discussed in detail in section \ref{p:members_leave_project}.
+
+As in most projects, the cancellation of funding by the investors can lead to failure or at least to a temporary stop of the project.
+
+Another possible risk is the research and development going into a wrong direction without getting recognized for a long time.
+Weekly jour fixes of all important project members and rigorous compliance with the quality assurance specifications shall overcome this risk.
+The quality manager plays an important role in this possible failure scenario.
+
+\subsubsection{Possible project support}
+The project team shall not define itself as a "closed circuit" but accept support from outside where it makes sense.
+If possible, contributors of similar projects, products, etc.
+can get involved into the research and development of the project.
+
+As the project proceeds and a more and more presentable solution evolves, other possible investors or contributors could be acquired.
+For the time being the public blog of the project can be used to communicate project success to the public, maybe later it is possible to practice a more extensive use of public relation tools an mechanisms to inform as many people as possible about the project.
+
+% team members leave the project
+\subsubsection{Risk of team members leaving the project}
+\label{p:members_leave_project}
+The actions to take when a team member leaves the project derive from section \ref{sect:team}. The quality assurance defines measures such as
+\begin{itemize}
+\item reviews,
+\item weekly jour fixes,
+\item extensive documentation of all work done within the project and
+\item tool support for intra-project communication.
+\end{itemize}
+These measures shall lead to a distribution of knowledge to as many team members as possible, so that no team member can get irreplaceable and project success can't get endangered by the drop out of a single person.
+The quality manager is responsible for controlling and reviewing the adherence of the quality assurance specifications.
+
+However, important team roles get back-upped by a second person. These are
+\begin{itemize}
+\item project manager,
+\item quality manager and
+\item security expert.
+\end{itemize}
 

### 2013-01-05 paper/mswp2012-proposal.tex
costs table and general stuff #1

@@
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+\usepackage[right]{eurosym}
 % \usepackage{mathptmx} % Times New Roman
@@
 
-\note{
-\begin{itemize}
-\item {\em Length: 2-3 pages}
-\item Rough estimation of cost in form of calculation (table(s)) + descriptive text.
-\item Justification for the personnel and non-personnel costs (equipment, material, travel and other costs)
-\item An Excel template is provided as supplementary material to support budgeting.
-\item Personnel costs
-	\begin{itemize}
-	\item     Justification for the personnel to be assigned to the project (type of position(s), description of nature of work, length and extent of involvement in the project)
-	\item     The application should include all persons who will be required for the proposed project (project lead, researchers, developers, advisory board, etc.).
+%\note{
+%\begin{itemize}
+%\item {\em Length: 2-3 pages}
+%\item Rough estimation of cost in form of calculation (table(s)) + descriptive text.
+%\item Justification for the personnel and non-personnel costs (equipment, material, travel and other costs)
+%\item An Excel template is provided as supplementary material to support budgeting.
+%\item Personnel costs
+%	\begin{itemize}
+%	\item     Justification for the personnel to be assigned to the project (type of position(s), description of nature of work, length and extent of involvement in the project)
+%	\item     The application should include all persons who will be required for the proposed project (project lead, researchers, developers, advisory board, etc.).
 The available legal categories of employment are contracts of employment for full- or part-time employees (DV) and reimbursement for work on an hourly basis (GB).
 In addition, a part-time contract of employment (DV 50\%, ``studentische Mitarbeiter'') may be requested for people who have not yet completed a Master or Diploma program (Diplom) in the relevant subject.
-	 \item    The justification of the requested personnel should contain:
-		\begin{itemize}
-		\item 	        description of type of work;
-		\item 		        extent of involvement (part-time contracts are permitted).
-		\end{itemize}
-	\item Exact numbers of employment categories can be found on the FWF Website (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
-	\end{itemize}
-\item Equipment costs
-	\begin{itemize}
-	\item     Indicate reasons for equipment costs.
+%	 \item    The justification of the requested personnel should contain:
+%		\begin{itemize}
+%		\item 	        description of type of work;
+%		\item 		        extent of involvement (part-time contracts are permitted).
+%		\end{itemize}
+%	\item Exact numbers of employment categories can be found on the FWF Website (\href{http://www.fwf.ac.at/de/projects/personalkostensaetze.html}{http://www.fwf.ac.at/de/projects/personalkostensaetze.html})
+%	\end{itemize}
+%\item Equipment costs
+%	\begin{itemize}
+%	\item     Indicate reasons for equipment costs.
 The ``scientific equipment'' category includes instruments, system components, costs for the use of software required by the project and other durable goods provided the cost per item (including VAT) exceeds EUR 1,500.00.
-	\end{itemize}
-\item Material costs
-	\begin{itemize}
-	\item     This category encompasses consumables and smaller pieces of equipment where the cost per item is below EUR 1,500.00 including VAT.
+%	\end{itemize}
+%\item Material costs
+%	\begin{itemize}
+%	\item     This category encompasses consumables and smaller pieces of equipment where the cost per item is below EUR 1,500.00 including VAT.
 The calculation of requested material costs should be justified with reference to the schedule, work plan and experimental plan.
 Experience with previous projects should be taken into account.
-	\end{itemize}
-\item Travel costs
-	\begin{itemize}
-	\item     Funding may be requested for the costs of project-specific travel and accommodation, field work, expeditions, etc.
+%	\end{itemize}
+%\item Travel costs
+%	\begin{itemize}
+%	\item     Funding may be requested for the costs of project-specific travel and accommodation, field work, expeditions, etc.
 Applicants are to provide a detailed travel (cost) plan broken down by project participant.
@@
 For longer stays an appropriate and comprehensible cost plan should be prepared.
-	\end{itemize}
-\item Other costs
-	\begin{itemize}
-	\item     Independent contracts for work and services (costs for work of clearly defined scope and content assigned to individuals, provided that this is scientifically justifiable and economical)
-    	\item     Costs that cannot be included under personnel, equipment, material or travel costs, such as:
-		\begin{itemize}
-		\item         reimbursement of costs towards or for the use of research facilities, e.g.
+%	\end{itemize}
+%\item Other costs
+%	\begin{itemize}
+%	\item     Independent contracts for work and services (costs for work of clearly defined scope and content assigned to individuals, provided that this is scientifically justifiable and economical)
+%    	\item     Costs that cannot be included under personnel, equipment, material or travel costs, such as:
+%		\begin{itemize}
+%		\item         reimbursement of costs towards or for the use of research facilities, e.g.
 of large-scale research facilities (project-specific 'equipment time').
 Applicants should obtain and submit multiple offers;
-		\item         costs for project-specific work carried out outside the applicant's research institution (e.g.
+%		\item         costs for project-specific work carried out outside the applicant's research institution (e.g.
 for analysis work performed elsewhere, for interviews, for sample collection, for preparation of thin slices etc.).
 Applicants should obtain and submit multiple offers;
-		\item         honoraria for test persons;
-		\end{itemize}
-	\end{itemize}
-\end{itemize}
-}
+%		\item         honoraria for test persons;
+%		\end{itemize}
+%	\end{itemize}
+%\end{itemize}
+%}
+
+\subsection{Personal costs}
+
+\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | p{2.5cm} | l |}
+\hline
+Member & Full-time / Part-time & Position & costs per hour & Duration & Overall costs \\
+\hline
+\hline
+project manager & FT & manager & & start - end & \\
+\hline
+co-project manager &  FT & manager & & start - end  & \\
+\hline
+quality manger & FT & manager & & start - end  & \\
+\hline
+strategy memeber 4 & FT &  middle-manager & & start with version 1.0  & \\
+\hline
+strategy memeber 4 & FT &  middle-manager &  & start with version 1.0  & \\
+\hline
+reserarcher 1 &  FT  & & & start - end   & \\
+\hline
+reserarcher 2 & FT  & & & start - end  & \\
+\hline
+reserarcher 3 & PT & & & start - end  & \\
+\hline
+reserarcher 4 & PT & & & middle - end & \\
+\hline
+reserarcher 5 & PT & & & middle - end &  \\
+\hline
+security expert & FT & & & start - end &  \\ 
+\hline
+usability \& design engineer 1 + 2 & FT & & & start - end  & \\
+\hline
+web dev 1 & FT & & & dev \& update & \\
+\hline
+web dev 2 & FT & &  & dev \& update & \\
+\hline
+web dev 3 & FT & &  & dev & \\
+\hline
+web dev 4 & FT & &  & dev & \\
+\hline
+mobile dev 1 & FT & &  & dev \& update & \\
+\hline
+mobile dev 2 & FT & &  & dev \& update & \\
+\hline
+mobile dev 3 & FT & &  & dev & \\
+\hline
+mobile dev 4 & FT & &  & dev & \\
+\hline
+\end{tabular}
+
+\subsection{Equipment}
+Workplace with licenses consisting of:
+
+\begin{itemize}
+	\item {Computer}
+	\item {Maus}
+	\item {Tastatur}
+	\item {Betriebssystem}
+	\item {IDE}
+	\item {...}
+\end{itemize}
+Makes around \EUR{1500} - \EUR{2000}  per employee. \\
+
+\subsection{Material}
+Once:\\
+Printer in the Office 3 $\times$ \EUR{1500} \\
+Testing devices (Android phones and iPhones) 4 $\times$ \EUR{500} \\
+Books for research and development about \EUR{500} \\
+Notebooks for managers 5 $\times$ \EUR{800} \\
+\\
+Monthly:\\
+Server \EUR{50} by renting mailserver, fileserver and repository \\
+Internet \EUR{50} \\
+\\
+
+\subsection{Travel}
+
+%hm, wieviele reisen sind nötig?
+
+\subsection{Miscellaneous}
+
+%--miete: 500€ monatlich? keine ahnung, wo liegen die preise?
+%--strom, 
+%telefon, 
+%wasser, 
+%heizung im büro
+%werbekosten für die gewinnung dre nutzer und partner: folder und sowas
+%befragung: vorbereitung, nen ort für die durchführung, die personen die teilnehmen sollten ne kleinigkeit bekommen, auswertung
+
+\pagebreak
 

### 2013-01-05 paper/mswp2012-proposal.tex
updated with costs

@@
 
-\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | p{2.5cm} | l |}
-\hline
-Member & Full-time / Part-time & Position & costs per hour & Duration & Overall costs \\
-\hline
-\hline
-project manager & FT & manager & & start - end & \\
-\hline
-co-project manager &  FT & manager & & start - end  & \\
-\hline
-quality manger & FT & manager & & start - end  & \\
-\hline
-strategy memeber 4 & FT &  middle-manager & & start with version 1.0  & \\
-\hline
-strategy memeber 4 & FT &  middle-manager &  & start with version 1.0  & \\
-\hline
-reserarcher 1 &  FT  & & & start - end   & \\
-\hline
-reserarcher 2 & FT  & & & start - end  & \\
-\hline
-reserarcher 3 & PT & & & start - end  & \\
-\hline
-reserarcher 4 & PT & & & middle - end & \\
-\hline
-reserarcher 5 & PT & & & middle - end &  \\
-\hline
-security expert & FT & & & start - end &  \\ 
-\hline
-usability \& design engineer 1 + 2 & FT & & & start - end  & \\
-\hline
-web dev 1 & FT & & & dev \& update & \\
-\hline
-web dev 2 & FT & &  & dev \& update & \\
-\hline
-web dev 3 & FT & &  & dev & \\
-\hline
-web dev 4 & FT & &  & dev & \\
-\hline
-mobile dev 1 & FT & &  & dev \& update & \\
-\hline
-mobile dev 2 & FT & &  & dev \& update & \\
-\hline
-mobile dev 3 & FT & &  & dev & \\
-\hline
-mobile dev 4 & FT & &  & dev & \\
+\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | l |}
+\hline
+Member & Full-time / Part-time & Position & Duration & Overall costs \\
+\hline
+\hline
+project manager 1 & FT & manager & start - end & \EUR{140.000} \\
+\hline
+co-project manager 2 &  FT & manager & start - end  & \EUR{130.000} \\
+\hline
+quality manger 3 & FT & manager & start - end  & \EUR{130.000} \\
+\hline
+marketing manager 1 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
+\hline
+marketing manager 2 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
+\hline
+reserarcher 1 &  FT  & employee & start - end  & \EUR{80.000} \\
+\hline
+reserarcher 2 & FT  & employee & start - end  & \EUR{80.000} \\
+\hline
+reserarcher 3 & PT & employee & start - end  & \EUR{40.000} \\
+\hline
+reserarcher 4 & PT & employee & middle - end & \EUR{20.000} \\
+\hline
+reserarcher 5 & PT & employee & middle - end & \EUR{20.000}  \\
+\hline
+security expert & FT & expert & start - end & \EUR{130.000}  \\ 
+\hline
+usability \& design engineer 1 & FT & employee & start - end  & \EUR{80.000} \\
+\hline
+usability \& design engineer 2  & FT & employee & start - end  & \EUR{80.000} \\
+\hline
+web dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
+\hline
+web dev 2 & FT & employee & dev \& update & \EUR{60.000} \\
+\hline
+web dev 3 & FT & employee & dev & \EUR{40.000} \\
+\hline
+web dev 4 & FT & employee & dev & \EUR{40.000} \\
+\hline
+mobile dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
+\hline
+mobile dev 2 & FT & employee & dev \& update & \EUR{60.000}  \\
+\hline
+mobile dev 3 & FT & employee & dev & \EUR{40.000} \\
+\hline
+mobile dev 4 & FT & employee & dev & \EUR{40.000} \\
 \hline
@@
 \subsection{Equipment}
-Workplace with licenses consisting of:
-
-\begin{itemize}
-	\item {Computer}
-	\item {Maus}
-	\item {Tastatur}
-	\item {Betriebssystem}
-	\item {IDE}
-	\item {...}
-\end{itemize}
-Makes around \EUR{1500} - \EUR{2000}  per employee. \\
+	\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} |}
+		\hline
+		workstation & member & costs \\
+		\hline
+		\hline
+		Computer &  &  \\
+		Maus &  &  \\
+		Keyboard &  &  \\
+		Display &  &  \\
+		OS &  &  \\
+		IDE &  &  \\
+		%&  &  \\
+		\hline
+	\end{tabular}
 
 \subsection{Material}
-Once:\\
-Printer in the Office 3 $\times$ \EUR{1500} \\
-Testing devices (Android phones and iPhones) 4 $\times$ \EUR{500} \\
-Books for research and development about \EUR{500} \\
-Notebooks for managers 5 $\times$ \EUR{800} \\
-\\
-Monthly:\\
-Server \EUR{50} by renting mailserver, fileserver and repository \\
-Internet \EUR{50} \\
-\\
+\begin{tabular}{| p{4cm} | p{2cm} | p{2cm} | p{2cm} | p{2cm} |}
+	\hline
+	name & amount & preparation & monthly & overall \\
+	\hline
+	\hline
+	%&&&&\\
+	%\hline
+	Testing devices & 4 & \EUR{500} & 0 & \EUR{500} \\
+	\hline
+	Books (research, dev) & NA & \EUR{500} & 0 & \EUR{500}\\
+	\hline
+	Notebooks & 5 & \EUR{800} & 0 & \\
+	\hline
+	Printer & 3 & \EUR{1500} & 0 &\\
+	\hline
+	Server & 1 & 200 & 50 &  \\
+	\hline
+	Internet & 1 & 50 & 50 &  \\
+	\hline
+\end{tabular}
+\\
+TODO: Explanation Text
 
 \subsection{Travel}
+
+das anwerben von partner benötigt einiges an reisen
+zum bewerben des projektes gehört gereist
+für die befragungen muss man an den ort der befragung reisen
 

### 2013-01-05 paper/mswp2012-proposal.tex
finished costs section

--- 2013-01-05 paper/mswp2012-proposal.tex
@@
 
-\begin{tabular}{| p{3cm} | p{2cm} | p{2cm} | p{2.5cm} | p{2.5cm} | l |}
-\hline
-Member & Full-time / Part-time & Position & costs per hour & Duration & Overall costs \\
-\hline
-\hline
-project manager & FT & manager & & start - end & \\
-\hline
-co-project manager &  FT & manager & & start - end  & \\
-\hline
-quality manger & FT & manager & & start - end  & \\
-\hline
-strategy memeber 4 & FT &  middle-manager & & start with version 1.0  & \\
-\hline
-strategy memeber 4 & FT &  middle-manager &  & start with version 1.0  & \\
-\hline
-reserarcher 1 &  FT  & & & start - end   & \\
-\hline
-reserarcher 2 & FT  & & & start - end  & \\
-\hline
-reserarcher 3 & PT & & & start - end  & \\
-\hline
-reserarcher 4 & PT & & & middle - end & \\
-\hline
-reserarcher 5 & PT & & & middle - end &  \\
-\hline
-security expert & FT & & & start - end &  \\ 
-\hline
-usability \& design engineer 1 + 2 & FT & & & start - end  & \\
-\hline
-web dev 1 & FT & & & dev \& update & \\
-\hline
-web dev 2 & FT & &  & dev \& update & \\
-\hline
-web dev 3 & FT & &  & dev & \\
-\hline
-web dev 4 & FT & &  & dev & \\
-\hline
-mobile dev 1 & FT & &  & dev \& update & \\
-\hline
-mobile dev 2 & FT & &  & dev \& update & \\
-\hline
-mobile dev 3 & FT & &  & dev & \\
-\hline
-mobile dev 4 & FT & &  & dev & \\
+Members take from human resources chapter \ref{sect:team}.\\
+\\
+\begin{tabular}{| p{3.5cm} | p{2cm} | p{3cm} | p{2.5cm} | r |}
+\hline
+Member & Full-time / Part-time & Position & Duration & Overall costs \\
+\hline
+\hline
+Project manager & FT & manager & start - end & \EUR{140.000} \\
+\hline
+Co-project manager &  FT & manager & start - end  & \EUR{130.000} \\
+\hline
+Quality manager & FT & manager & start - end  & \EUR{130.000} \\
+\hline
+Marketing manager 1 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
+\hline
+Marketing manager 2 & FT &  middle-manager  & last 6 months  & \EUR{32.000} \\
+\hline
+Researcher 1 &  FT  & employee & start - end  & \EUR{80.000} \\
+\hline
+Researcher 2 & FT  & employee & start - end  & \EUR{80.000} \\
+\hline
+Researcher 3 & PT & employee & start - end  & \EUR{40.000} \\
+\hline
+Researcher 4 & PT & employee & middle - end & \EUR{20.000} \\
+\hline
+Researcher 5 & PT & employee & middle - end & \EUR{20.000}  \\
+\hline
+Security expert & FT & expert & start - end & \EUR{130.000}  \\ 
+\hline
+Usability- \& Design engineer 1 & FT & employee & start - end  & \EUR{80.000} \\
+\hline
+Usability- \& Design engineer 2  & FT & employee & start - end  & \EUR{80.000} \\
+\hline
+Web dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
+\hline
+Web dev 2 & FT & employee & dev \& update & \EUR{60.000} \\
+\hline
+Web dev 3 & FT & employee & dev & \EUR{40.000} \\
+\hline
+Web dev 4 & FT & employee & dev & \EUR{40.000} \\
+\hline
+Mobile dev 1 & FT & employee & dev \& update & \EUR{60.000} \\
+\hline
+Mobile dev 2 & FT & employee & dev \& update & \EUR{60.000}  \\
+\hline
+Mobile dev 3 & FT & employee & dev & \EUR{40.000} \\
+\hline
+Mobile dev 4 & FT & employee & dev & \EUR{40.000} \\
 \hline
 \end{tabular}
+\\
+\\
+Overall costs for personal: \EUR{1.454.000}
 
 \subsection{Equipment}
-Workplace with licenses consisting of:
-
-\begin{itemize}
-	\item {Computer}
-	\item {Maus}
-	\item {Tastatur}
-	\item {Betriebssystem}
-	\item {IDE}
-	\item {...}
-\end{itemize}
-Makes around \EUR{1500} - \EUR{2000}  per employee. \\
+
+About 22 Workstations.
+\begin{itemize}
+		\item{Computer}
+		\item{Maus}
+		\item{Keyboard}
+		\item{Two Displays}
+		\item{OS (License)}
+		\item{IDE (License)}
+		\item{Office (License)}
+\end{itemize} 
+	\begin{tabular}{| p{2cm} | p{6cm} | r |}
+		\hline
+		Workstation & Member & Costs \\
+		\hline
+		\hline
+		01 & project manager   & \EUR{1.200} \\
+		\hline
+		02 & co-project manager  & \EUR{1.200} \\
+		\hline
+		03 & quality manger  & \EUR{1.500} \\
+		\hline
+		04 & marketing manager 1 & \EUR{1.200} \\
+		\hline
+		05 & marketing manager 2 & \EUR{1.200} \\
+		\hline
+		06 & researcher 1 &  \EUR{1.200} \\
+		\hline
+		07 & researcher 2 &  \EUR{1.200} \\
+		\hline
+		08 & researcher 3 &  \EUR{1.200} \\
+		\hline
+		09 & researcher 4 &  \EUR{1.200} \\
+		\hline
+		10 & researcher 5 &  \EUR{1.200} \\
+		\hline
+		11 & security expert  &  \EUR{1.800} \\
+		\hline
+		12 & usability \& design engineer 1 & \EUR{2.000} \\
+		\hline
+		13 & usability \& design engineer 2 & \EUR{2.000} \\
+		\hline
+		14 & web dev 1 &  \EUR{1.500} \\
+		\hline
+		15 & web dev 2 &  \EUR{1.500} \\
+		\hline
+		16 & web dev 3 &  \EUR{1.500} \\
+		\hline
+		17 & web dev 4 &  \EUR{1.500} \\
+		\hline
+		18 & mobile dev 1 &  \EUR{1.500} \\
+		\hline
+		19 & mobile dev 2 &  \EUR{1.500} \\
+		\hline
+		20 & mobile dev 3 &  \EUR{1.500} \\
+		\hline
+		21 & mobile dev 4 &  \EUR{1.500} \\
+		\hline
+		22 &  spare & \EUR{1.500} \\
+		%&  &  \\
+		\hline
+	\end{tabular}
+\\
+\\
+Total costs for equipment: \EUR{30.400}.
 
 \subsection{Material}
-Once:\\
-Printer in the Office 3 $\times$ \EUR{1500} \\
-Testing devices (Android phones and iPhones) 4 $\times$ \EUR{500} \\
-Books for research and development about \EUR{500} \\
-Notebooks for managers 5 $\times$ \EUR{800} \\
-\\
-Monthly:\\
-Server \EUR{50} by renting mailserver, fileserver and repository \\
-Internet \EUR{50} \\
-\\
-
+\begin{tabular}{| p{4cm} | p{2cm} | p{2cm} | p{2cm} | r |}
+	\hline
+	Name & Amount & Preparation & Monthly & Overall \\
+	\hline
+	\hline
+	Testing devices & 4 & \EUR{500} & 0 & \EUR{2.000} \\
+	\hline
+	Books (research, dev) & budget & \EUR{500} & 0 & \EUR{500}\\
+	\hline
+	Manager notebooks  & 5 & \EUR{800} & 0 & \EUR{4.000} \\
+	\hline
+	Laserprinter & 1 & \EUR{1500} & 0 & \EUR{1.500}  \\
+	\hline
+	Photoprinter & 1 & \EUR{500} & 0 & \EUR{500}  \\
+	\hline
+	Copystation \& Scanner & 1 & \EUR{1000} & 0 & \EUR{1.000}  \\
+	\hline
+	Server & 1 &  \EUR{200} &  \EUR{50} &  \EUR{1.600}   \\
+	\hline
+\end{tabular}
+\\
+\\
+Total costs for material: \EUR{11.100}. \\
+\\
+Runtime of the whole project is 28 months. Therefore monthly for the server is 28 time \EUR{50}. \\
+\\
+Hosted server with functionalities:
+\begin{itemize}
+	\item{Mailing}
+	\item{Fileserver}
+	\item{Webserver}
+	\item{Database}
+	\item{Repository}
+	\item{Ticket-System (Bugtracker)}
+\end{itemize}
 \subsection{Travel}
-
-%hm, wieviele reisen sind nötig?
-
+Given are the pool sizes of money for a specific task.\\
+\begin{tabular}{| p{4cm} | r |}
+	\hline
+	Type & Cost \\
+	\hline
+	\hline
+	Interview & \EUR{15.000} \\
+	\hline
+	Advertisement & \EUR{50.000} \\
+	\hline
+	Recruitment of partners & \EUR{35.000} \\
+	\hline
+\end{tabular}
+\\
+\\
+Total costs travel: \EUR{100.000}.
 \subsection{Miscellaneous}
-
-%--miete: 500€ monatlich? keine ahnung, wo liegen die preise?
-%--strom, 
-%telefon, 
-%wasser, 
-%heizung im büro
-%werbekosten für die gewinnung dre nutzer und partner: folder und sowas
-%befragung: vorbereitung, nen ort für die durchführung, die personen die teilnehmen sollten ne kleinigkeit bekommen, auswertung
+\begin{tabular}{| p{4cm} | p{2cm} | p{2cm} | r |}
+	\hline
+	name & preparation & monthly & overall \\
+	\hline
+	\hline
+	Internet \& Telephone &  \EUR{50} &  \EUR{50} & \EUR{1.450}  \\
+	\hline
+	Rent & \EUR{0} & \EUR{1.800} & \EUR{50.400} \\
+	\hline
+	Furnishment & \EUR{15.000} & \EUR{0} & \EUR{15.000} \\
+	\hline
+	Flyer, Folders & \EUR{0} & \EUR{200} & \EUR{5.600} \\
+	\hline
+\end{tabular}
+\\
+\\
+Total costs for miscellaneous: \EUR{72.450}.\\
+\\
+Rent calculation is given by a space consumption of 8 $m^2$ for the first employee and 6 $m^2$ for every following one.\\
+This gives us a total needed space of 130 $m^2$.
+
+\subsection{Overall listing}
+
+\begin{tabular}{| p{4cm} | r |}
+	\hline
+	Area & Costs \\
+	\hline
+	\hline
+	Personal & \EUR{1.454.000}  \\
+	\hline
+	Equipment & \EUR{30.400} \\
+	\hline
+	Material & \EUR{11.100} \\
+	\hline
+	Travel & \EUR{100.000}\\
+	\hline
+	Miscellaneous & \EUR{72.450}\\
+	\hline
+	\hline
+	Overall Project & \EUR{1.667.950} \\
+	\hline
+\end{tabular}
 

### 2013-01-10 paper/mswp2012-proposal.tex
added Communication Lines

@@
 
-The \textbf{project manager} will be the head of the project and will be assisted by his co project manager during all phases and as a backup in case of unforseeable circuumstances.
-One of them should also have a funded technical knowledge, the other expirenced in economical topics.
-Both should work as a team and also handle the ressource management and trigger the planned phases.
-\\
-
-Another very importent rule to fill will be the \textbf{Quality manager}.
+The \textbf{project manager} will be the head of the project and will be assisted by his co project manager during all phases and as a backup in case of unforeseeable circumstances.
+One of them should also have a funded technical knowledge, the other experienced in economical topics.
+Both should work as a team and also handle the resource management and trigger the planned phases.
+\\
+
+Another very important rule to fill will be the \textbf{Quality manager}.
 This person will create the quality plan, organize reviews and check, if the corresponding plan is also executed like intended.
@@
 \subsubsection{Dev Team}
-There will be several Dev Teams with different main aspects to cover, but whatsoever there will be couple of poeple that will be responsible for small parts of each team.
+There will be several Dev Teams with different main aspects to cover, but whatsoever there will be couple of people that will be responsible for small parts of each team.
 
@@
 
-Additional a \textbf{Mobile Dev Team} will join to implment mobile clients for the project.
+Additional a \textbf{Mobile Dev Team} will join to implement mobile clients for the project.
 Only iOS and Android clients are planned until version 2.0 therefore knowledge in iOS and/or Android programming is mandatory.
@@
 \subsubsection{Communication and Documentation}
-For each team there will be a seperate mailing list to distribute messages to the whole team.
+For each team there will be a separate mailing list to distribute messages to the whole team.
 
@@
 
-The official blog will be used as communication channel to the users and the community and will also be used to publish scientifical relevant results from the research group as well as results from user interviews.
+The official blog will be used as communication channel to the users and the community and will also be used to publish scientifically relevant results from the research group as well as results from user interviews.
 \\
@@
 This tool will be set up by the strategy team before the project start.
+\\
+
+All members of every project team has to satisfy the line of communication.
+Every requests or problems should be discussed within the team and with the responsible team leader.
+Project leader itself will handle the requests from their team members or forward the problem to the project manager.
+If a big problem comes into being, it will be redirected to the management of the company.
 
